### 2022-07-15 ersteops/templates/printpdf/rendered_template.tex
add print_pdf app

% my_prescription_latex.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{ifthen}
\usepackage[abs]{overpic}
\usepackage{pict2e,xcolor,varwidth}
\usepackage{color}
\usepackage{layout}
\usepackage[paperwidth=14cm, paperheight=22.5cm, left=0.0cm,right=0.5cm,top=3.3in,bottom=2.2in,headheight=3in,headsep=0pt,footskip=120pt]{geometry}
% Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
%
\graphicspath{ {/vagrant/dev/petstore/static/img/printpdf/} }
\usepackage{fancyhdr}

% Dont break up words
\hyphenpenalty 10000
\exhyphenpenalty 10000

\pagestyle{fancy}
\fancyhf{}
% Define Header content
% fancyhead[C] image center
% fancyhead[L] image left
% fancyhead[L] image right
\fancyhead[C]{
    % Transparent head image
    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_head.png}
    % Hospital Logo
    % \put(10,45){
    %     % Logo Image
    %     hospital_logo.jpg
    % }
    % Consulta    
    % \put(68,65){\parbox[t]{6cm}{\textsf{\large{
    %    \textbf{Consulta \#:} 95
    % }
    % }}}    
    % Date    
    \put(68,65){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Fecha:} 07, Jun 2018
    }
    }}}    
    % Patient
    \put(68,60){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Paciente:} pelotitas
    }
    }}}
    % Species / Breed
    \put(68,50){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Especie:} Gato / siames nordico
    }
    }}}
    % Sex
    \put(68,40){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Sexo:} Hembra
    }
    }}}
    % weight
    \put(68,35){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Peso:} 6.0
    }
    }}}
    % Dueño
    \put(68,30){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Responsable:} Lillian Garcia
    }
    }}}
    % Edad
    \put(68,20){\parbox[t]{6cm}{\textsf{\large{
       \textbf{Edad:} 0 año,  meses
    }
    }}}
    % Diagnostico
    \put(10,5){\parbox[t]{10cm}{\textsf{\large{
       \textbf{Diagnostico Presuntivo:} esta es una nueva mascota de cero
    }
    }}}
    % Tratamiento
    \put(10,-5){\parbox[t]{10cm}{\textsf{\large{
       \textbf{Tratamiento:}
    }
    }}}                            
    % \put(70,42){\parbox[l]{4.2cm}{\textsf{\large{
    %    \textbf{Sexo:} Hembra
    % }
    % }}}
    % Pet Gender
    % \put(70,30){
    % \textsf{
    % \large{
    % \textbf{
    % Sexo:
    % }
    % Hembra
    % }
    % }
    % }
    % Pet weight
    % \put(70,25){
    % \textsf{
    % \large{
    % \textbf{
    % Peso:
    % }
    % 6.0
    % }
    % }
    % }        
    % % Informacion
    % \put(65,70){\parbox{4.2cm}{\textsf{
    %     Edad: Jan. 7, 2018
    % }}}
    % % Diagnostico
    % \put(10,16){\parbox{7cm}{\textsf{
    %     Diagnostico Presuntivo: esta es una nueva mascota de cero
    % }}}
    \end{overpic}
}
% End Header

% Begin Footer content
% fancyfoot[C] image center
% fancyfoot[L] image left
% fancyfoot[L] image right
\fancyfoot[L]{
    % Add grid param after unit to adjust text position over image
    % Transparent foot image
    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_foot.png}
    \put(1,5){
        \includegraphics[width=4cm, height=4cm]{qr_signature}
    }
    % Medic Signature
    % \put(50,33){\textsl{\textbf{\parbox[t]{2.4in}{
    %     {\fontfamily{frc}\selectfont
    %         \normalsize{ Medico Responsable: Juan ManuelRivero Mercado }
    %     }
    % }}}}
    % Medic
    \put(45,25){\parbox[t]{10cm}{\textsf{
       \textbf{Veterinario: } Juan Manuel Rivero Mercado
    }}}
    % Cedula
    \put(45,20){\parbox[t]{10cm}{\textsf{
       \textbf{Cedula Profesional: } 9999999999
    }}}
    \put(45,15){\parbox[t]{10cm}{\textsf{
        \textbf{ UNAM } 
    }}}
    % Medic Right
    % position <left, right(+5)>
    % \put(131,60){\textsf{\textsl{\parbox{2.65in}{
    %     
    % }}}}
    % % Telefono
    % \put(131,50){\textsf{\parbox{2.65in}{
    %     \textbf{Contacto} 
    % }}}
    % % Cedula Profesional
    % \put(131,40){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula profesional} 
    % }}}
    % % Cedula Especialidad
    % \put(131,35){\textsf{\parbox{2.65in}{
    %     \textbf{Cédula especialidad} 
    % }}}
    % %Especialidad ,Alma Mater
    % \put(131.5,27){\textsf{\textbf{\parbox{2.65in}{
    %      , 
    % }}}}
    % % Sello electronico
    % \put(10,15){\textsf{
    %     \textbf{Sello electrónico:} 
    % }}
    % Footer prescrypto
    % Need try color here
    % \put(45,5){\textsf{\textbf{
    %     LAAM Vaterinarios
    % }}}
    \end{overpic}
}
% End footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist
\begin{document}
    % Include Background in ./prescript/media/media/template_v1.pdf
    \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
    % Define page content
    \textsf{\large{
    \begin{changemargin}{1.5cm}{1.2cm}
        \begin{enumerate}
            \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
        \end{enumerate}
        % Indicaciones Extra
        % \begin{enumerate}
        %     \textbf{Indicaciones Extra: \\ } \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
        % \end{enumerate}
    \end{changemargin}
    }}
\end{document}

### 2022-07-15 ersteops/printpdf/urls.py

@@ -1,0 +1,17 @@
+# log/urls.py
+from django.conf.urls import url
+from . import views
+# Use login.
+from django.contrib.auth.decorators import login_required
+#from petfile.views import AddPetFileVisit, PetFileVisitList, PetFileVisitReview, PetFileVisitDetail
+from printpdf.views import document_as_pdf, document_as_pdf_print
+# We are adding a URL called /home
+urlpatterns = [
+    #url(r'^$', login_required(AddPetFileVisit.as_view(), login_url='/login/'), name="agregar consulta"),
+    #url(r'^review/$',login_required(PetFileVisitList.as_view(), login_url='/login/'), name="petfilevisit"),
+    #url(r'^review/(?P<pk>[0-9]+)/$',login_required(PetFileVisitReview.as_view(), login_url='/login/'), name="petfilevisitdetail"),
+    #url(r'^petfile/(?P<pk>[0-9]+)/$',login_required(PetFileVisitDetail.as_view(), login_url='/login/'), name="petfilevisitdetail"),
+    #url(r'^(?P<pk>[0-9]+)/$', login_required(document_as_pdf), name='pdf-generate'),
+    url(r'^(?P<pk>[0-9]+)/$', login_required(document_as_pdf), name='pdf-generate'),
+	url(r'^(?P<pk>[0-9]+)/print/$', login_required(document_as_pdf_print), name='pdf-print-generate'),
+]

### 2022-07-15 ersteops/printpdf/views.py

@@ -1,0 +1,216 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+from django.shortcuts import render
+# Django
+from django.conf import settings
+# Python general
+from django.template.loader import get_template
+from django.template import Context , Template
+from django.http import HttpResponse
+from django.shortcuts import redirect
+# Messages
+from django.contrib import messages
+# Latex specific
+from subprocess import Popen, PIPE
+#import tempfile
+#from backports import tempfile
+import tempfile
+import os
+import ast
+import unicodedata
+from petfile.views import get_petfile_json
+from django.conf import settings
+import os.path
+
+# Create your views here.
+# generate pdf for screen
+def document_as_pdf(request,pk):
+  # Get document data
+  user = request.user
+  params = get_petfile_json(request, pk)
+  print params
+  # Generate QR Signature
+  #generate_qr(signature)
+  # Clean params strings
+  params = escape_params(params)
+  params['diagnostic'] = (params['diagnostic'][:250]+ '...') if len(params['diagnostic']) > 250 else params['diagnostic']
+  # print "***************** diagnostic "
+  # print params['diagnostic']
+  # print "***************** diagnostic end "
+  #print params
+  generate_tex(params,'pdf')
+  tempdir = settings.BASE_DIR+'/templates/printpdf/'
+  tex_file = settings.BASE_DIR+'/templates/printpdf/rendered_template'
+
+  if generate_pdf(tempdir,tex_file):    
+    print "PDF Generated Ok"
+    pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
+    pdf = pdf_file.read()
+    r = HttpResponse(content_type='application/pdf')
+    r.write(pdf)
+    return r
+  else:
+    print "PDF Error!!! ckeck /templates/printpdf/rendered_template.log" 
+    messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
+    return redirect('/petfile/review/')
+
+def document_as_pdf_print(request,pk):
+  # Get document data
+  user = request.user
+  params = get_petfile_json(request, pk)
+  print params
+  # Generate QR Signature
+  #generate_qr(signature)
+  # Clean params strings
+  params = escape_params(params)
[…]

### 2022-07-15 ersteops/paperless/models.py
fix typo

@@ -242,7 +242,7 @@ class MedicalReport(models.Model):
             res = []
         return res
     
-    def json_inmovilization_type(type):
+    def json_inmovilization_type(self):
         #convert_to_json
         try:
             res = list(eval(self.inmovilization_type))

### 2022-07-15 ersteops/paperless/models.py
clean model

@@ -260,29 +260,5 @@ class MedicalReport(models.Model):
     def __str__(self):
         return "{}, {}, {}, {}".format(unicodedata.normalize('NFKD',str(self.id)),unicodedata.normalize('NFKD', self.odoo_client), unicodedata.normalize('NFKD', self.patient_name), self.created_at)
 
-# class PhysicalExploration(models.Model):
-#     time = models.DateTimeField("Dia/Hora",blank= True, null =True)
-#     heart_rate = models.CharField("Frequencia Cardiaca", max_length=20,default='', blank=True)
-#     respiratory_rate = models.CharField("Frequencia Respiratoria", max_length=20,default='', blank=True)
-#     blood_pressure = models.CharField("Presion Arterial", max_length=20,default='', blank=True)
-#     temperature = models.CharField("Temperature", max_length=20,default='', blank=True)
-#     oxygen_saturation = models.CharField("Saturacion O2", max_length=20,default='', blank=True)
-#     glucometry = models.CharField("Glucometria", max_length=20,default='', blank=True)
-#     glassgow_motor = models.CharField("Glassgow Motor", max_length=20,default='', blank=True)
-#     glassgow_verbal = models.CharField("Glassgow Verbal", max_length=20,default='', blank=True)
-#     glassgow_ocular = models.CharField("Glassgow Ocular", max_length=20,default='', blank=True)
-#     glassgow_final = models.CharField("Glassgow Final", max_length=20,default='', blank=True)
 
-#     created_at = models.DateTimeField("Fecha de alta",auto_now_add=True,editable=False)
-#     last_modified = models.DateTimeField("Última modificación",auto_now=True,editable=False)
-
-#     class Meta:
-#         verbose_name_plural = "Exploracion Fisica"
-#         ordering = ['created_at']
-
-#     def __str__(self):
-#         return "{}, {}, {}, {}".format(unicodedata.normalize('NFKD',str(self.id)), self.created_at)
-
-
-#class Medications(models.Model):
 

### 2022-08-04 ersteops/templates/printpdf/rendered_template.tex
add volatile files

@@
 \usepackage{layout}
-\usepackage[paperwidth=14cm, paperheight=22.5cm, left=0.0cm,right=0.5cm,top=3.3in,bottom=2.2in,headheight=3in,headsep=0pt,footskip=120pt]{geometry}
+\usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
 % Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
 %
-\graphicspath{ {/vagrant/dev/petstore/static/img/printpdf/} }
+\graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
 \usepackage{fancyhdr}
+%Definitions from inkscape
+\makeatletter%
+\providecommand\color[2][]{%
+ \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
+ \renewcommand\color[2][]{}%
+}%
+\providecommand\transparent[1]{%
+ \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
+ \renewcommand\transparent[1]{}%
+}%
+\providecommand\rotatebox[2]{#2}%
+\newcommand*\fsize{\dimexpr\f@size pt\relax}%
+\newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
+\ifx\svgwidth\undefined%
+ \setlength{\unitlength}{792bp}%
+ \ifx\svgscale\undefined%
+   \relax%
+ \else%
+   \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
+ \fi%
+\else%
+ \setlength{\unitlength}{\svgwidth}%
+\fi%
+\global\let\svgwidth\undefined%
+\global\let\svgscale\undefined%
+\makeatother%
+\lineheight{1}%
+\setlength\tabcolsep{0pt}%
+%endDefinitions from inkscape
 
@@
     % Transparent head image
-    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_head.png}
+    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_head.png}
     % Hospital Logo
@@
     % }
-    % Consulta    
-    % \put(68,65){\parbox[t]{6cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 95
-    % }
-    % }}}    
+    Consulta    
+    \put(1,1){\parbox[t]{6cm}{\textsf{\large{
+       \textbf{Consulta \#:} 1
+    }
+    }}}
+
+    \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido}\end{tabular}}}}%
+
     % Date    
     \put(68,65){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Fecha:} 07, Jun 2018
+       %\textbf{Fecha:} 
     }
@@
     \put(68,60){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Paciente:} pelotitas
+       %\textbf{Paciente:} 
     }
@@
     \put(68,50){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Especie:} Gato / siames nordico
+       %\textbf{Especie:}  / 
     }
@@
     \put(68,40){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Sexo:} Hembra
+       %\textbf{Sexo:} 
     }
@@
     \put(68,35){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Peso:} 6.0
+       %\textbf{Peso:} 
     }
@@
     \put(68,30){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Responsable:} Lillian Garcia
+       %\textbf{Responsable:} 
     }
@@
     \put(68,20){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Edad:} 0 año,  meses
+       %\textbf{Edad:}  año,  meses
     }
@@
     \put(10,5){\parbox[t]{10cm}{\textsf{\large{
-       \textbf{Diagnostico Presuntivo:} esta es una nueva mascota de cero
+       %\textbf{Diagnostico Presuntivo:} 
     }
@@
     \put(10,-5){\parbox[t]{10cm}{\textsf{\large{
-       \textbf{Tratamiento:}
+       %\textbf{Tratamiento:}
     }
@@
     % \put(70,42){\parbox[l]{4.2cm}{\textsf{\large{
-    %    \textbf{Sexo:} Hembra
+    %    \textbf{Sexo:} 
     % }
@@
     % }
-    % Hembra
+    % 
     % }
@@
     % }
-    % 6.0
+    % 
     % }
@@
     % \put(65,70){\parbox{4.2cm}{\textsf{
-    %     Edad: Jan. 7, 2018
+    %     Edad: 
     % }}}
@@
     % \put(10,16){\parbox{7cm}{\textsf{
-    %     Diagnostico Presuntivo: esta es una nueva mascota de cero
+    %     Diagnostico Presuntivo: 
     % }}}
@@
     % Transparent foot image
-    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/dev/petstore/templates/printpdf/transparent_foot.png}
+    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_foot.png}
     \put(1,5){
@@
     %     {\fontfamily{frc}\selectfont
-    %         \normalsize{ Medico Responsable: Juan ManuelRivero Mercado }
+    %         \normalsize{ Medico Responsable:  }
     %     }
@@
     \put(45,25){\parbox[t]{10cm}{\textsf{
-       \textbf{Veterinario: } Juan Manuel Rivero Mercado
+       %\textbf{Veterinario: } 
     }}}
@@
     \put(45,20){\parbox[t]{10cm}{\textsf{
-       \textbf{Cedula Profesional: } 9999999999
+       %\textbf{Cedula Profesional: } 
     }}}
     \put(45,15){\parbox[t]{10cm}{\textsf{
-        \textbf{ UNAM } 
+        %\textbf{  } 
     }}}
@@
         \begin{enumerate}
-            \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
+            %
+            bla!
         \end{enumerate}
@@
         % \begin{enumerate}
-        %     \textbf{Indicaciones Extra: \\ } \item \textbf{Bordetella[ Vacuna Canina]} \qquad dsd sdfsdf df sdf
+        %     \textbf{Indicaciones Extra: \\ } 
         % \end{enumerate}

### 2022-08-04 ersteops/printpdf/views.py
fix logic for vidauno

@@ -18,22 +18,31 @@ import tempfile
 import os
 import ast
 import unicodedata
-from petfile.views import get_petfile_json
+#from petfile.views import get_petfile_json
 from django.conf import settings
 import os.path
+
+from paperless.dict_fields import MedicalReportDict
+from paperless.models import MedicalReport
+
+# Logging library
+import logging
+logger = logging.getLogger('django_info')
+
 
 # Create your views here.
 # generate pdf for screen
 def document_as_pdf(request,pk):
   # Get document data
   user = request.user
-  params = get_petfile_json(request, pk)
-  print params
+  params = get_medical_report(pk)
+
+  print(params)
   # Generate QR Signature
   #generate_qr(signature)
   # Clean params strings
   params = escape_params(params)
-  params['diagnostic'] = (params['diagnostic'][:250]+ '...') if len(params['diagnostic']) > 250 else params['diagnostic']
+  #params['diagnostic'] = (params['diagnostic'][:250]+ '...') if len(params['diagnostic']) > 250 else params['diagnostic']
   # print "***************** diagnostic "
   # print params['diagnostic']
   # print "***************** diagnostic end "
@@ -43,27 +52,29 @@ def document_as_pdf(request,pk):
   tex_file = settings.BASE_DIR+'/templates/printpdf/rendered_template'
 
   if generate_pdf(tempdir,tex_file):    
-    print "PDF Generated Ok"
+    #print("PDF Generated Ok")
+    logger.info('[ PRINTPDF! - PDF Generated OK]')
     pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
     pdf = pdf_file.read()
     r = HttpResponse(content_type='application/pdf')
     r.write(pdf)
     return r
   else:
-    print "PDF Error!!! ckeck /templates/printpdf/rendered_template.log" 
+    #print("PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
+    logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     return redirect('/petfile/review/')
 
 def document_as_pdf_print(request,pk):
   # Get document data
   user = request.user
-  params = get_petfile_json(request, pk)
-  print params
[…]

### 2022-08-04 ersteops/ersteops/urls.py
add path

@@ -19,4 +19,5 @@ urlpatterns = [
     # Jet Dashboard
     url(r'^jet/', include('jet.urls','jet')),
     url(r'^jet/dashboard/', include('jet.dashboard.urls','jet-dashboard')),
+    url(r'^printpdf/', include('printpdf.urls')),
 ]+ static(settings.STATIC_URL, document_root=settings.STATIC_ROOT)

### 2022-08-04 ersteops/printpdf/views.py
upddate redirect

@@ -63,7 +63,7 @@ def document_as_pdf(request,pk):
     #print("PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
-    return redirect('/petfile/review/')
+    return redirect('/paperless/')
 
 def document_as_pdf_print(request,pk):
   # Get document data

### 2022-08-04 ersteops/paperless/dict_fields.py
update dict

@@ -68,4 +68,11 @@ MedicalReportDict = {
 "derivation_type": [],
 "demarcation_responsable": "",
 "demarcation_relation": "",
+"electro_qrs":"",
+"email": "",
+"send_email":"",
+"derivation_hospital": "",
+"crum_hospital":"",
+"crum_notes":"",
+"notes":"",
 }

### 2022-08-04 ersteops/paperless/models.py
update model

@@ -187,6 +187,14 @@ class MedicalReport(models.Model):
     electro_abnormalities = models.CharField("Anormalidades", blank=True, default='', max_length=100)
     electro_interpretation = models.TextField("Interpretacion", blank=True, default='') 
 
+    electro_qrs = models.CharField("QRS", blank=True, default='', max_length=20)
+    email = models.CharField("Email", blank=True, default='', max_length=50)
+    send_email = models.CharField("Se envio Email", blank=True, default='', max_length=20)
+    derivation_hospital = models.CharField("Hospitar derivacion", blank=True, default='', max_length=100)
+    crum_hospital = models.CharField("Hospitar recibe CRUM", blank=True, default='', max_length=100)
+    crum_notes = models.TextField("Notas Crum",blank=True)
+    notes = models.TextField("Notas Emergencia",blank=True)  
+
     def json_physical_exploration(self):
         #convert_to_json
         try:

### 2022-08-11 ersteops/ersteops/settings.py
add email variables

@@ -295,3 +295,10 @@ CHANNEL_LAYERS = {
     },
 }
 
+EMAIL_BACKEND = os.environ['EMAIL_BACKEND']
+EMAIL_HOST = os.environ['EMAIL_HOST']
+EMAIL_HOST_USER = os.environ['EMAIL_HOST_USER']
+EMAIL_HOST_PASSWORD = os.environ['EMAIL_HOST_PASSWORD'] #past the key or password app here
+EMAIL_PORT = os.environ['EMAIL_PORT']
+EMAIL_USE_TLS = os.environ['EMAIL_USE_TLS']
+DEFAULT_FROM_EMAIL = os.environ['DEFAULT_FROM_EMAIL']

### 2022-08-11 ersteops/paperless/dict_fields.py
update dict fields

@@ -75,4 +75,17 @@ MedicalReportDict = {
 "crum_hospital":"",
 "crum_notes":"",
 "notes":"",
+"detail_pat_history_daibetes_melitus":"",
+"detail_pat_history_arterial_hypertension":"",
+"detail_pat_history_heart_disease":"",
+"detail_pat_history_pneumopathies":"",
+"detail_pat_history_trauma":"",
+"detail_pat_history_alergy":"",
+"det_normal_head":"",
+"det_normal_face":"",
+"det_normal_torax":"",
+"det_normal_abdomen":"",
+"det_normal_limbs":"",
+"det_normal_genitals":"",
+"det_normal_spine":"",
 }

### 2022-08-11 ersteops/paperless/models.py
add detail fields

@@ -126,17 +126,29 @@ class MedicalReport(models.Model):
     other_traumatics = models.CharField('Otro Traumatico', max_length=50, default= '', blank=True, choices=TRAUMATICS)
     airway = models.TextField('Via Aerea', default= '', blank=True )
     other_airway = models.CharField('Otra Via Aerea', max_length=20, default= '', blank=True, choices=AIRWAY)
-    # (physical_exploration = pe)
+    
     physical_exploration = models.TextField("Exploracion Fisica",blank=True, default='')
     medications = models.TextField("Medicamentos",blank=True, default='')
     # Normal
+    # (physical_exploration = pe)
     normal_head = models.CharField("Cabeza", blank=True, default='', max_length=10, choices=YES_NO)
     normal_face = models.CharField("Face", blank=True, default='', max_length=10, choices=YES_NO)
+    normal_neck = models.CharField("Cuello", blank=True, default='', max_length=10, choices=YES_NO)
     normal_torax = models.CharField("Tórax", blank=True, default='', max_length=10, choices=YES_NO)
     normal_abdomen = models.CharField("Abdomen", blank=True, default='', max_length=10, choices=YES_NO)
     normal_limbs = models.CharField("Extremidades", blank=True, default='', max_length=10, choices=YES_NO)
     normal_genitals = models.CharField("Genitales", blank=True, default='', max_length=10, choices=YES_NO)
     normal_spine = models.CharField("Columna Vertebral", blank=True, default='', max_length=10, choices=YES_NO)
+
+    det_normal_head = models.TextField("Notas Cabeza", blank=True)
+    det_normal_face = models.TextField("Notas Cara", blank=True)
+    det_normal_neck = models.TextField("Notas Cuello", blank=True)    
+    det_normal_torax = models.TextField("Notas Tórax", blank=True)
+    det_normal_abdomen = models.TextField("Notas Abdomen", blank=True)
+    det_normal_limbs = models.TextField("Notas Extremidades", blank=True)
+    det_normal_genitals = models.TextField("Notas Genitales", blank=True)
+    det_normal_spine = models.TextField("Notas Columna Vertebral", blank=True)
+
 
     current_condition = models.TextField("Padecimiento Actual",blank=True)
 
@@ -153,6 +165,13 @@ class MedicalReport(models.Model):
     pathological_history_trauma = models.CharField("Quirurgicos/Trauma",blank= True, default=False,max_length=10, choices=YES_NO)
[…]

### 2022-08-11 ersteops/paperless/views.py
add detail fields to post action

@@ -25,7 +25,7 @@ from django.views.decorators.csrf import csrf_exempt, csrf_protect
 from django.http import JsonResponse
 import json
 #def emergency_data_dict(emergency):
-
+from django.core.mail import EmailMessage
 
 #@method_decorator(login_required, name='dispatch')
 class MedicalReportNew(View):
@@ -308,18 +308,29 @@ def new_medicalreport(request):
           demarcation_responsable = vue_data['demarcation_responsable'],
           demarcation_relation = vue_data['demarcation_relation'],
           user = request.user,
+          electro_qrs = vue_data['electro_qrs'],
+          email = vue_data['email'],
+          send_email = vue_data['send_email'],
+          derivation_hospital = vue_data['derivation_hospital'],
+          crum_hospital = vue_data['crum_hospital'],
+          crum_notes = vue_data['crum_notes'],
+          notes = vue_data['notes'],
+          detail_pat_history_daibetes_melitus = vue_data['detail_pat_history_daibetes_melitus'],
+          detail_pat_history_arterial_hypertension = vue_data['detail_pat_history_arterial_hypertension'],
+          detail_pat_history_heart_disease = vue_data['detail_pat_history_heart_disease'],
+          detail_pat_history_pneumopathies = vue_data['detail_pat_history_pneumopathies'],
+          detail_pat_history_trauma = vue_data['detail_pat_history_trauma'],
+          detail_pat_history_alergy = vue_data['detail_pat_history_alergy'],
+          det_normal_head = vue_data['det_normal_head'],
+          det_normal_face = vue_data['det_normal_face'],
+          det_normal_torax = vue_data['det_normal_torax'],
+          det_normal_abdomen = vue_data['det_normal_abdomen'],
+          det_normal_limbs = vue_data['det_normal_limbs'],
+          det_normal_genitals = vue_data['det_normal_genitals'],
+          det_normal_spine = vue_data['det_normal_spine'],
           )
           messages.error(request, "Parte Medico Guardado correctamente!!!")
-          # if data['timer_type'] == '1':
-          #     emergency.unit_dispatched_time = timezone.now()
-          # if data['timer_type'] == '2':
-          #     emergency.arrival_time = timezone.now()
-          #     emergency.attention_time = timezone.now()
-          # if data['timer_type'] == '3':
-          #     emergency.derivation_time = timezone.now()
[…]

### 2022-08-11 ersteops/printpdf/views.py
update template name

@@ -30,6 +30,7 @@ import logging
 logger = logging.getLogger('django_info')
 
 
+
 # Create your views here.
 # generate pdf for screen
 def document_as_pdf(request,pk):
@@ -111,11 +112,14 @@ def generate_medication_tex(params):
 
 def generate_tex(params,output_mode):
   # Assign template
+  #Takes tex input from the directory templates/printpdf
+  #the pdf-background comes from /static/img/printpdf
   latex_hospital_logo = "hospital_logo.jpg"
   if output_mode == 'pdf':
-    template = get_template('printpdf/petstore_recip_template.tex')
+    #template = get_template('printpdf/petstore_recip_template.tex')
+    template = get_template('printpdf/paperless_template.tex')
   else:
-    template = get_template('printpdf/petstore_recip_template_print.tex')
+    template = get_template('printpdf/paperless_template_print.tex')
   # Define header and footer
   latex_overpic_head = '\\begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{'+ settings.BASE_DIR +'/templates/printpdf/transparent_head.png}'
   latex_overpic_foot = '\\begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{'+ settings.BASE_DIR +'/templates/printpdf/transparent_foot.png}'

### 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
add updated files

@@
-% my_prescription_latex.tex
+%prescription_latex.tex
 
@@
 \usepackage{layout}
+%\usepackage{tikz}
+%\usepackage{relsize}
+\usepackage{etoolbox}
 \usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
@@
 \graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
-\usepackage{fancyhdr}
-%Definitions from inkscape
+%\setmainfont{Arial}
+%\usepackage{fancyhdr}
+\usepackage{uarial}
+%\usepackage[scaled]{uarial}
+\usepackage{transparent}
+\usepackage[protrusion=true,expansion=true]{microtype}
+\usepackage{calc}
+\usepackage{verbatim}
+\makeatletter
+\g@addto@macro\@verbatim\small
+\makeatother 
+\usepackage{xcolor}
+
+\usepackage{lmodern}
+%\fontfamily{lmss}\selectfont
+
+\begin{document}
+\fontfamily{lmss}\selectfont
+    % Include Background in ./prescript/media/media/template_v1.pdf
+    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
+    % Define page content
+    %\textsf{\large{
+    %\begin{changemargin}{1.5cm}{1.2cm}
+        %\begin{enumerate}
+            %
+            %bla!
+        %\end{enumerate}
+    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
+    %    \textbf{Consulta \#:} 7
+    % }
+    % }}}
+        % Indicaciones Extra
+        % \begin{enumerate}
+        %     \textbf{Indicaciones Extra: \\ } 
+        % \end{enumerate}
+    %\end{changemargin}
+    %}}
+    % \begin{picture}(1,0.77272727)%
+    %     %Consulta    
+    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
+    %    \textbf7
+    % }
+    % }}}
+    % \end{picture}
+% \begingroup%
+%   \makeatletter%
+%   \providecommand\color[2][]{%
+%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
+%     \renewcommand\color[2][]{}%
+%   }%
+%   \providecommand\transparent[1]{%
+%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
+%     \renewcommand\transparent[1]{}%
+%   }%
+%   \providecommand\rotatebox[2]{#2}%
+%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
+%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
+%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
+%   \ifx\svgwidth\undefined%
+%     \setlength{\unitlength}{792bp}%
+%     \ifx\svgscale\undefined%
+%       \relax%
+%     \else%
+%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
+%     \fi%
+%   \else%
+%     \setlength{\unitlength}{\svgwidth}%
+%   \fi%
+%   \global\let\svgwidth\undefined%
+%   \global\let\svgscale\undefined%
+%   \makeatother%
+%   \begin{picture}(1,0.77272727)%
+%     \lineheight{1}%
+%     \setlength\tabcolsep{0pt}%
+%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%
+
+%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
+%     %    \textbf{Consulta \#:} 7
+%     % }
+%     % }}}
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 7 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 7 }\end{tabular}}}}%
+%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
+
+%   \end{picture}%
+% \endgroup%
+
+\begin{figure}
+  \centering
+  \def\svgwidth{\columnwidth}
+  %\input{paperless_template_6.pdf_tex}
+
+\begingroup%
   \makeatletter%
@@
   \ifx\svgwidth\undefined%
- \setlength{\unitlength}{792bp}%
+    \setlength{\unitlength}{782.27360219bp}%
     \ifx\svgscale\undefined%
@@
   \makeatother%
+  \begin{picture}(1,0.77245213)%
     \lineheight{1}%
     \setlength\tabcolsep{0pt}%
-%endDefinitions from inkscape
+    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
 
-% Dont break up words
-\hyphenpenalty 10000
-\exhyphenpenalty 10000
+    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
+    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
 
-\pagestyle{fancy}
-\fancyhf{}
-% Define Header content
-% fancyhead[C] image center
-% fancyhead[L] image left
-% fancyhead[L] image right
-\fancyhead[C]{
-    % Transparent head image
-    \begin{overpic}[width=13.5cm,height=7cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_head.png}
-    % Hospital Logo
-    % \put(10,45){
-    %     % Logo Image
-    %     hospital_logo.jpg
-    % }
-    Consulta    
-    \put(1,1){\parbox[t]{6cm}{\textsf{\large{
-       \textbf{Consulta \#:} 1
-    }
-    }}}
+    %Paciente
+    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
+    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
+    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
+    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 82\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
-    \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido}\end{tabular}}}}%
+    %Paciente desconocido
+    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
+    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
-    % Date    
-    \put(68,65){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Fecha:} 
-    }
-    }}}    
-    % Patient
-    \put(68,60){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Paciente:} 
-    }
-    }}}
-    % Species / Breed
-    \put(68,50){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Especie:}  / 
-    }
-    }}}
-    % Sex
-    \put(68,40){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Sexo:} 
-    }
-    }}}
-    % weight
-    \put(68,35){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Peso:} 
-    }
-    }}}
-    % Dueño
-    \put(68,30){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Responsable:} 
-    }
-    }}}
-    % Edad
-    \put(68,20){\parbox[t]{6cm}{\textsf{\large{
-       %\textbf{Edad:}  año,  meses
-    }
-    }}}
-    % Diagnostico
-    \put(10,5){\parbox[t]{10cm}{\textsf{\large{
-       %\textbf{Diagnostico Presuntivo:} 
-    }
-    }}}
-    % Tratamiento
-    \put(10,-5){\parbox[t]{10cm}{\textsf{\large{
-       %\textbf{Tratamiento:}
-    }
-    }}}                            
-    % \put(70,42){\parbox[l]{4.2cm}{\textsf{\large{
-    %    \textbf{Sexo:} 
-    % }
-    % }}}
-    % Pet Gender
-    % \put(70,30){
-    % \textsf{
-    % \large{
-    % \textbf{
-    % Sexo:
-    % }
-    % 
-    % }
-    % }
-    % }
-    % Pet weight
-    % \put(70,25){
-    % \textsf{
-    % \large{
-    % \textbf{
-    % Peso:
-    % }
-    % 
-    % }
-    % }
-    % }        
-    % % Informacion
-    % \put(65,70){\parbox{4.2cm}{\textsf{
-    %     Edad: 
-    % }}}
-    % % Diagnostico
-    % \put(10,16){\parbox{7cm}{\textsf{
-    %     Diagnostico Presuntivo: 
-    % }}}
-    \end{overpic}
-}
-% End Header
+    %Padecimiento
+    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
-% Begin Footer content
-% fancyfoot[C] image center
-% fancyfoot[L] image left
-% fancyfoot[L] image right
-\fancyfoot[L]{
-    % Add grid param after unit to adjust text position over image
-    % Transparent foot image
-    \begin{overpic}[width=13.5cm,height=5cm,unit=1mm]{/vagrant/ersteops/templates/printpdf/transparent_foot.png}
-    \put(1,5){
-        \includegraphics[width=4cm, height=4cm]{qr_signature}
-    }
-    % Medic Signature
-    % \put(50,33){\textsl{\textbf{\parbox[t]{2.4in}{
-    %     {\fontfamily{frc}\selectfont
-    %         \normalsize{ Medico Responsable:  }
-    %     }
-    % }}}}
-    % Medic
-    \put(45,25){\parbox[t]{10cm}{\textsf{
-       %\textbf{Veterinario: } 
-    }}}
-    % Cedula
-    \put(45,20){\parbox[t]{10cm}{\textsf{
-       %\textbf{Cedula Profesional: } 
-    }}}
-    \put(45,15){\parbox[t]{10cm}{\textsf{
-        %\textbf{  } 
-    }}}
-    % Medic Right
-    % position <left, right(+5)>
-    % \put(131,60){\textsf{\textsl{\parbox{2.65in}{
-    %     
-    % }}}}
-    % % Telefono
-    % \put(131,50){\textsf{\parbox{2.65in}{
-    %     \textbf{Contacto} 
-    % }}}
-    % % Cedula Profesional
-    % \put(131,40){\textsf{\parbox{2.65in}{
-    %     \textbf{Cédula profesional} 
-    % }}}
-    % % Cedula Especialidad
-    % \put(131,35){\textsf{\parbox{2.65in}{
-    %     \textbf{Cédula especialidad} 
-    % }}}
-    % %Especialidad ,Alma Mater
-    % \put(131.5,27){\textsf{\textbf{\parbox{2.65in}{
-    %      , 
-    % }}}}
-    % % Sello electronico
-    % \put(10,15){\textsf{
-    %     \textbf{Sello electrónico:} 
-    % }}
-    % Footer prescrypto
-    % Need try color here
-    % \put(45,5){\textsf{\textbf{
-    %     LAAM Vaterinarios
-    % }}}
-    \end{overpic}
-}
-% End footer
-\renewcommand{\headrulewidth}{0pt}
-\renewcommand{\footrulewidth}{0pt}
+    %Antecedentes
+    %Diabetes
+    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
+    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
+    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
+    %Hipertension
+    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
+    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
+    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
 
-\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
-\let\endchangemargin=\endlist
-\begin{document}
-    % Include Background in ./prescript/media/media/template_v1.pdf
-    \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
-    % Define page content
-    \textsf{\large{
-    \begin{changemargin}{1.5cm}{1.2cm}
-        \begin{enumerate}
-            %
-            bla!
-        \end{enumerate}
-        % Indicaciones Extra
-        % \begin{enumerate}
-        %     \textbf{Indicaciones Extra: \\ } 
-        % \end{enumerate}
-    \end{changemargin}
-    }}
+  \end{picture}
+\endgroup%
+\end{figure}
+
+\newpage
+
+\begin{figure}
+  \centering
+  \def\svgwidth{\columnwidth}
+  %\input{paperless_template_6.pdf_tex}
+
+\begingroup%
+  \makeatletter%
+  \providecommand\color[2][]{%
+    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
+    \renewcommand\color[2][]{}%
+  }%
+  \providecommand\transparent[1]{%
+    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
+    \renewcommand\transparent[1]{}%
+  }%
+  \providecommand\rotatebox[2]{#2}%
+  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
+  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
+  \ifx\svgwidth\undefined%
+    \setlength{\unitlength}{782.27360219bp}%
+    \ifx\svgscale\undefined%
+      \relax%
+    \else%
+      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
+    \fi%
+  \else%
+    \setlength{\unitlength}{\svgwidth}%
+  \fi%
+  \global\let\svgwidth\undefined%
+  \global\let\svgscale\undefined%
+  \makeatother%
+  \begin{picture}(1,0.77245213)%
+    \lineheight{1}%
+    \setlength\tabcolsep{0pt}%
+    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
+
+    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
+    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
+
+    %Paciente
+    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
+    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
+    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
+    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 82\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+
+    %Paciente desconocido
+    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
+    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+
+    %Padecimiento
+    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+
+    %Antecedentes
+    %Diabetes
+    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
+    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
+    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
+    %Hipertension
+    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
+    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
+    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
+
+  \end{picture}
+\endgroup%
+\end{figure}
+
 \end{document}

### 2022-08-11 ersteops/templates/printpdf/paperless_template.tex
add tex template

--- 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
@@
 %prescription_latex.tex
-
+{% autoescape on %}
 \documentclass{article}
@@
 % Check parameters in: https://en.wikibooks.org/wiki/LaTeX/Page_Layout
-%
-\graphicspath{ {/vagrant/ersteops/static/img/printpdf/} }
+%{# Define where latex finds images #}
+{{ latex_graphics_path }}
 %\setmainfont{Arial}
@@
         %\begin{enumerate}
-            %
+            %{{ all_medications }}
             %bla!
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 7
+    %    \textbf{Consulta \#:} {{ content.id }}
     % }
@@
         % \begin{enumerate}
-        %     \textbf{Indicaciones Extra: \\ } 
+        %     \textbf{Indicaciones Extra: \\ } {{ all_medications }}
         % \end{enumerate}
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf7
+    %    \textbf{{ content.id }}
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 7
+%     %    \textbf{Consulta \#:} {{ content.id }}
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 7 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 7 }\end{tabular}}}}%
-%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido {{content.id}} }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.id}} }\end{tabular}}}}%
+%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit }} }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit_type}} }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit_plate}} }\end{tabular}}}}%
 
@@
 
-    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
+    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
+    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%
 
     %Paciente
-    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
-    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 82\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
+    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_phone}}\end{tabular}}}}%
+    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
+    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
-    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
-    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{conten.patient_unknow}}\end{tabular}}}}%
+    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
+    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
+    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
 
@@
 \end{document}
+{% endautoescape %}

### 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
add pdf generation before sending email

@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 7
+    %    \textbf{Consulta \#:} 14
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf7
+    %    \textbf14
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 7
+%     %    \textbf{Consulta \#:} 14
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 7 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 7 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 14 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 14 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
 %     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-001 }\end{tabular}}}}%
 
@@
    	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%
 
@@
     \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 82\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 59\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lotzo Sanchez Jaime\end{tabular}}}}%
     \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont se lastimo saltando del auto\end{tabular}}}}%
 

### 2022-08-11 ersteops/paperless/views.py

@@ -26,6 +26,8 @@ from django.http import JsonResponse
 import json
 #def emergency_data_dict(emergency):
 from django.core.mail import EmailMessage
+import os.path
+from printpdf.views import document_as_new_pdf
 
 #@method_decorator(login_required, name='dispatch')
 class MedicalReportNew(View):
@@ -329,8 +331,8 @@ def new_medicalreport(request):
           det_normal_genitals = vue_data['det_normal_genitals'],
           det_normal_spine = vue_data['det_normal_spine'],
           )
-          messages.error(request, "Parte Medico Guardado correctamente!!!")
-          Send_Mail_To(vue_data['email'])
+          messages.info(request, "Parte Medico Guardado correctamente!!!")
+          Send_Mail_To(request,vue_data['email'],medicalReport.id)
           # emergency.save()
           data.update({'status': 'success', 'client_id':qs.odoo_client})
           response = JsonResponse(data)
@@ -353,14 +355,23 @@ def find_on_list(my_list_Dict, what_to_search):
   return my_text
 
 
-def Send_Mail_To(email_recive):
+def Send_Mail_To(request,email_recive,pk):
+
   try:
     email = EmailMessage(
-      'Hello',
-      'Body goes here',
+      'Parte Medico Vida uno subject',
+      'Este es su parte medico body',
       'info@keepitsimple.com.mx',
       [ email_recive, ]
     )
+    pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.pdf/'
+    tempdir = settings.BASE_DIR+'/templates/printpdf/'
+    pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
+    pdf = document_as_new_pdf(request,pk)
+    email.attach('Parte_Medico_Vida_Uno.pdf',pdf,'application/pdf')
+    #pdf_to_attach = os.path.join(tempdir, 'rendered_template.pdf')
+    #email.attach_file(pdf_to_attach)
+
     email.send()
     logger.info('[ NEW MEWDICAL SEndMail : {} ]'.format(email_recive))
   except Exception as e:

### 2022-08-11 ersteops/printpdf/views.py

@@ -66,6 +66,40 @@ def document_as_pdf(request,pk):
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     return redirect('/paperless/')
 
+def document_as_new_pdf(request,pk):
+  # Get document data
+  user = request.user
+  params = get_medical_report(pk)
+
+  print(params)
+  # Generate QR Signature
+  #generate_qr(signature)
+  # Clean params strings
+  params = escape_params(params)
+  #params['diagnostic'] = (params['diagnostic'][:250]+ '...') if len(params['diagnostic']) > 250 else params['diagnostic']
+  # print "***************** diagnostic "
+  # print params['diagnostic']
+  # print "***************** diagnostic end "
+  #print params
+  generate_tex(params,'pdf')
+  tempdir = settings.BASE_DIR+'/templates/printpdf/'
+  tex_file = settings.BASE_DIR+'/templates/printpdf/rendered_template'
+
+  if generate_pdf(tempdir,tex_file):    
+    #print("PDF Generated Ok")
+    logger.info('[ PRINTPDF! - PDF Generated OK]')
+    pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
+    pdf = pdf_file.read()
+    #r = HttpResponse(content_type='application/pdf')
+    #r.write(pdf)
+    return pdf
+  else:
+    #print("PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
+    logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
+    messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
+    return redirect('/paperless/')
+
+
 def document_as_pdf_print(request,pk):
   # Get document data
   user = request.user
@@ -96,6 +130,7 @@ def document_as_pdf_print(request,pk):
     logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     return redirect('/petfile/review/')
+
 
 
 

### 2022-08-11 ersteops/paperless/views.py
add some comments and fix filename with paperless_id

@@ -349,6 +349,7 @@ def new_medicalreport(request):
 # /Update Timer Functionality
 
 def find_on_list(my_list_Dict, what_to_search):
+  #define Yes or No if key is on dict
   my_text='No'
   if my_list_Dict.count(what_to_search) > 0:
     my_text = 'Si'
@@ -356,7 +357,7 @@ def find_on_list(my_list_Dict, what_to_search):
 
 
 def Send_Mail_To(request,email_recive,pk):
-
+  #Send mail via smtp gmail server
   try:
     email = EmailMessage(
       'Parte Medico Vida uno subject',
@@ -368,6 +369,7 @@ def Send_Mail_To(request,email_recive,pk):
     tempdir = settings.BASE_DIR+'/templates/printpdf/'
     pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
     pdf = document_as_new_pdf(request,pk)
+    file_name = 'Parte_Medico_Vida_Uno_{}.pdf'.format(str(pk))
     email.attach('Parte_Medico_Vida_Uno.pdf',pdf,'application/pdf')
     #pdf_to_attach = os.path.join(tempdir, 'rendered_template.pdf')
     #email.attach_file(pdf_to_attach)

### 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
add crew data and validation

--- 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 7
+    %    \textbf{Consulta \#:} 16
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf7
+    %    \textbf16
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 7
+%     %    \textbf{Consulta \#:} 16
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 7 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 7 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 16 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 16 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ NA }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ NA }\end{tabular}}}}%
 
@@
     \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
@@
     \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 82\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 15\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SHEEE Sanchez Jaime\end{tabular}}}}%
     \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

### 2022-08-11 ersteops/paperless/models.py

@@ -212,7 +212,11 @@ class MedicalReport(models.Model):
     derivation_hospital = models.CharField("Hospitar derivacion", blank=True, default='', max_length=100)
     crum_hospital = models.CharField("Hospitar recibe CRUM", blank=True, default='', max_length=100)
     crum_notes = models.TextField("Notas Crum",blank=True)
-    notes = models.TextField("Notas Emergencia",blank=True)  
+    notes = models.TextField("Notas Emergencia",blank=True)
+    crew_medic = models.CharField("Medico CREW",blank=True,default='',max_length=50)
+    crew_medic_id_card = models.CharField("Cedula Profesional",blank=True,default='',max_length=50)
+    crew_tum = models.CharField("TUM",blank=True,default='',max_length=50)
+    crew_operator = models.CharField("Operador",blank=True,default='',max_length=50) 
 
     def json_physical_exploration(self):
         #convert_to_json

### 2022-08-11 ersteops/paperless/views.py

@@ -330,6 +330,10 @@ def new_medicalreport(request):
           det_normal_limbs = vue_data['det_normal_limbs'],
           det_normal_genitals = vue_data['det_normal_genitals'],
           det_normal_spine = vue_data['det_normal_spine'],
+          crew_medic = vue_data['crew_medic'],
+          crew_medic_id_card = vue_data['crew_medic_id_card'],
+          crew_tum = vue_data['crew_tum'],
+          crew_operator = vue_data['crew_operator'],
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
           Send_Mail_To(request,vue_data['email'],medicalReport.id)

### 2022-08-17 ersteops/ersteops/settings.py
add parameters to use S3 Storage

@@ -302,3 +302,24 @@ EMAIL_HOST_PASSWORD = os.environ['EMAIL_HOST_PASSWORD'] #past the key or passwor
 EMAIL_PORT = os.environ['EMAIL_PORT']
 EMAIL_USE_TLS = os.environ['EMAIL_USE_TLS']
 DEFAULT_FROM_EMAIL = os.environ['DEFAULT_FROM_EMAIL']
+
+
+MEDIA_LOCAL = ast.literal_eval(os.environ['PDF_MEDIA_LOCAL'])
+# Define if media storage is local or S3
+if MEDIA_LOCAL:
+  MEDIA_ROOT = os.path.join(BASE_DIR, 'media/')
+  MEDIA_URL = os.path.join(BASE_DIR, 'media/')
+else:
+  # AWS S3 Settings
+  AWS_STORAGE_BUCKET_NAME = os.environ['PDF_AWS_STORAGE_BUCKET_NAME']
+  AWS_ACCESS_KEY_ID = os.environ['PDF_AWS_ACCESS_KEY_ID']
+  AWS_SECRET_ACCESS_KEY = os.environ['PDF_AWS_SECRET_ACCESS_KEY']
+  AWS_S3_CUSTOM_DOMAIN = '%s.s3.amazonaws.com' % AWS_STORAGE_BUCKET_NAME
+  # AWS Config
+  MEDIAFILES_LOCATION = 'media'
+  MEDIA_URL = "https://%s/%s/" % (AWS_S3_CUSTOM_DOMAIN, MEDIAFILES_LOCATION)
+  #DEFAULT_FILE_STORAGE = 'ersteops.custom_storages.MediaStorage' 
+  DEFAULT_FILE_STORAGE = 'storages.backends.s3boto3.S3Boto3Storage'
+  AWS_S3_FILE_OVERWRITE = False
+  AWS_DEFAULT_ACL = None
+  

### 2022-08-17 ersteops/ersteops/urls.py
add media to urls

@@ -20,4 +20,4 @@ urlpatterns = [
     url(r'^jet/', include('jet.urls','jet')),
     url(r'^jet/dashboard/', include('jet.dashboard.urls','jet-dashboard')),
     url(r'^printpdf/', include('printpdf.urls')),
-]+ static(settings.STATIC_URL, document_root=settings.STATIC_ROOT)
+]+ static(settings.STATIC_URL, document_root=settings.STATIC_ROOT) + static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)

### 2022-08-17 ersteops/paperless/dict_fields.py
update dict

@@ -83,9 +83,14 @@ MedicalReportDict = {
 "detail_pat_history_alergy":"",
 "det_normal_head":"",
 "det_normal_face":"",
+"det_normal_neck":"",
 "det_normal_torax":"",
 "det_normal_abdomen":"",
 "det_normal_limbs":"",
 "det_normal_genitals":"",
 "det_normal_spine":"",
+"crew_medic":"",
+"crew_medic_id_card":"",
+"crew_tum":"",
+"crew_operator":"",
 }

### 2022-08-17 ersteops/paperless/models.py
add field to store pdf on aws s3

@@ -3,6 +3,7 @@ from django.db import models
 from django.contrib.auth.models import User
 import unicodedata
 import json
+from django.core.validators import FileExtensionValidator
 # Create your models here.
 
 class MedicalReport(models.Model):
@@ -217,6 +218,8 @@ class MedicalReport(models.Model):
     crew_medic_id_card = models.CharField("Cedula Profesional",blank=True,default='',max_length=50)
     crew_tum = models.CharField("TUM",blank=True,default='',max_length=50)
     crew_operator = models.CharField("Operador",blank=True,default='',max_length=50) 
+    final_report = models.FileField("archivo de estudios(pdf o jpg)",validators=[FileExtensionValidator(allowed_extensions=['pdf','jpg'])],max_length=100,upload_to="pdffile/pdf_files",default="",blank=True)
+
 
     def json_physical_exploration(self):
         #convert_to_json

### 2022-08-17 ersteops/paperless/views.py
add pdf logic

@@ -29,6 +29,8 @@ from django.core.mail import EmailMessage
 import os.path
 from printpdf.views import document_as_new_pdf
 
+from django.core.files.base import ContentFile, File
+
 #@method_decorator(login_required, name='dispatch')
 class MedicalReportNew(View):
   template_name = "paperless/new_medical_report_vue.html"
@@ -265,6 +267,7 @@ def new_medicalreport(request):
           physical_exploration= vue_data['physical_exploration'], 
           normal_head= find_on_list(vue_data['normal_elements'],'Cabeza'), 
           normal_face= find_on_list(vue_data['normal_elements'],'Cara'), 
+          normal_neck= find_on_list(vue_data['normal_elements'],'Cuello'), 
           normal_torax= find_on_list(vue_data['normal_elements'],'Tórax'), 
           normal_abdomen= find_on_list(vue_data['normal_elements'],'Abdomen'), 
           normal_limbs= find_on_list(vue_data['normal_elements'],'Extremidades'), 
@@ -325,6 +328,7 @@ def new_medicalreport(request):
           detail_pat_history_alergy = vue_data['detail_pat_history_alergy'],
           det_normal_head = vue_data['det_normal_head'],
           det_normal_face = vue_data['det_normal_face'],
+          det_normal_neck = vue_data['det_normal_neck'],          
           det_normal_torax = vue_data['det_normal_torax'],
           det_normal_abdomen = vue_data['det_normal_abdomen'],
           det_normal_limbs = vue_data['det_normal_limbs'],
@@ -337,6 +341,12 @@ def new_medicalreport(request):
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
           Send_Mail_To(request,vue_data['email'],medicalReport.id)
+          tempdir = settings.BASE_DIR+'/templates/printpdf/'
+          pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
+          pdf = pdf_file.read()
+          file_name = 'Parte_Medico_Vida_Uno_{}.pdf'.format(str(medicalReport.id))
+          medicalReport.final_report.save(file_name,ContentFile(pdf))
+          #medicalReport.save()
           # emergency.save()
           data.update({'status': 'success', 'client_id':qs.odoo_client})
           response = JsonResponse(data)
[…]

### 2022-08-17 ersteops/templates/printpdf/paperless_template.tex
update

@@
 %\fontfamily{lmss}\selectfont
+\usepackage[utf8]{inputenc}
+%\usepackage{unixode}
 
@@
 
-    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%
+    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
+    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%
 
     %Paciente
-    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
+    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
     \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_phone}}\end{tabular}}}}%
-    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%
+    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{conten.patient_unknow}}\end{tabular}}}}%
-    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
-    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
-    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%
+    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_unknow}}\end{tabular}}}}%
+    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
+    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
+    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
+    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
+
+    %Generales
+    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.attention_place}} \end{tabular}}}}%
+    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_type}} \end{tabular}}}}%
+    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.event_type}} \end{tabular}}}}%
+    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.traumatics}} \end{tabular}}}}%
+    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo:{{content.pupil_state_left}}\end{tabular}}}}%
+    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {{content.pupil_state_right}}\end{tabular}}}}%
+    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.consultation_reason}}\end{tabular}}}}%
+    %to_fix
+
+    %Medicamentos (to_fix)
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ content.medications|truncatechars:20}}\end{tabular}}}}%
 
@@
     %Diabetes
-    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
-    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
-    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
+    \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
+    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_daibetes_melitus}}\end{tabular}}}}%
+    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_daibetes_melitus}}\end{tabular}}}}%
     %Hipertension
-    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
-    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
-    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
+    \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
+    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_arterial_hypertension}}\end{tabular}}}}%
+    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_arterial_hypertension}}\end{tabular}}}}%
+    %Cardiopatias
+    \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
+    \put(0.63928128,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_heart_disease}} \end{tabular}}}}%
+    \put(0.59572153,0.48073243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_heart_disease}} \end{tabular}}}}%
+    %Neumopatias
+    \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
+    \put(0.63928128,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_pneumopathies}}\end{tabular}}}}%
+    \put(0.59572153,0.45747395){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_pneumopathies}}\end{tabular}}}}%
+    %Trauma
+    \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
+    \put(0.63928128,0.43527803){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_trauma}}\end{tabular}}}}%
+    \put(0.59572153,0.43421546){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_trauma}}\end{tabular}}}}%
+    %Alergy
+    \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
+    \put(0.63928128,0.41201958){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_alergy}}\end{tabular}}}}%
+    \put(0.59572153,0.410957){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_alergy}}\end{tabular}}}}%
+    %Other
+    \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
+    \put(0.63928128,0.38876109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.other_pathological_history}}\end{tabular}}}}%
+    %\put(0.59572153,0.38769855){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
 
+    %Exploracion Fisica
+    %Cabeza
+    \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
+    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_head}}\end{tabular}}}}%
+    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_head}}\end{tabular}}}}%
+    %Cara
+    \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
+    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_face}}\end{tabular}}}}%
+    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_face}}\end{tabular}}}}%
+    %Cuello
+    \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
+    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_neck}}\end{tabular}}}}%
+    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_neck}}\end{tabular}}}}%
+    %Torax
+    \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
+    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_torax}}\end{tabular}}}}%
+    \put(0.57421341,0.26602505){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_torax}}\end{tabular}}}}%
+    %Abdomen
+    \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
+    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_abdomen}}\end{tabular}}}}%
+    \put(0.57421363,0.24991392){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_abdomen}}\end{tabular}}}}%
+    %Extremidades
+    \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
+    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_limbs}}\end{tabular}}}}%
+    \put(0.59031192,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_limbs}}\end{tabular}}}}%
+    %Genitales
+    \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
+    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_genitals}}\end{tabular}}}}%
+    \put(0.58368309,0.21763312){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_genitals}}\end{tabular}}}}%
+    %Columna
+    \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
+    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_spine}}\end{tabular}}}}%
+    \put(0.58218801,0.19630385){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_spine}}\end{tabular}}}}%
+    %Electro
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_pr}}\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_st}}\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qt}}\end{tabular}}}}%
+    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
+    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
+    %Signos Vitales 1
+    \put(0.48899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:31\end{tabular}}}}%
+    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
+    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 121\end{tabular}}}}%
+    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 122\end{tabular}}}}%
+    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 123\end{tabular}}}}%
+    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 124\end{tabular}}}}%
+    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 125\end{tabular}}}}%
+    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 126\end{tabular}}}}%
+    %Signos Vitales 2
+    \put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
+    \put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
+    \put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
+    \put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
+    \put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
+    \put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
+    \put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
+    \put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
   \end{picture}
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
-
-    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%
-
-    %Paciente
-    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
-    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_phone}}\end{tabular}}}}%
-    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%
-
-    %Paciente desconocido
-    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{conten.patient_unknow}}\end{tabular}}}}%
-    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
-    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
-    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%
-
-    %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
-
-    %Antecedentes
-    %Diabetes
-    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
-    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
-    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
-    %Hipertension
-    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
-    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
-    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
+    %Impresion diagnostica
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.treatment}}\end{tabular}}}}%
+    %Tratamiento
+    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.diagnostic_impresion}}\end{tabular}}}}%
+    %Derivacion
+    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_type}}\end{tabular}}}}%
+    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
+    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.state_of_health}}\end{tabular}}}}%
+    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_recive}}\end{tabular}}}}%
+    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_amount}}\end{tabular}}}}%
+    %Finalizacion
+    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_relation}}\end{tabular}}}}%
+    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic}}\end{tabular}}}}%
+    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic_id_card}}\end{tabular}}}}%
+    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_tum}}\end{tabular}}}}%
+    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_operator}}\end{tabular}}}}%
+    \put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X1 }}\end{tabular}}}}%
+    \put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+    \put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
 

### 2022-08-17 ersteops/templates/printpdf/rendered_template.tex
update

--- 2022-08-11 ersteops/templates/printpdf/rendered_template.tex
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 14
+    %    \textbf{Consulta \#:} 34
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf14
+    %    \textbf34
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 14
+%     %    \textbf{Consulta \#:} 34
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 14 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 14 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 34 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 34 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
@@
 
-    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%
+    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
+    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%
 
     %Paciente
-    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
+    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
     \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 59\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lotzo Sanchez Jaime\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 45\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Nika Sanchez Jaime\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont luiis spota\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
-    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
-    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont paciente desconocido y asi\end{tabular}}}}%
+    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  la filiacion desconocida\end{tabular}}}}%
+    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont pantalon rojo rotio\end{tabular}}}}%
+    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rojo rojo amarillo\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont se lastimo saltando del auto\end{tabular}}}}%
+    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%
+
+    %Generales
+    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hogar \end{tabular}}}}%
+    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Urgencias \end{tabular}}}}%
+    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Traumaticos \end{tabular}}}}%
+    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Craneal\textquotesingle , \textquotesingle Craneoencefalico\textquotesingle ] \end{tabular}}}}%
+    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo:[\textquotesingle Isocoria\textquotesingle , \textquotesingle Midriasis\textquotesingle ]\end{tabular}}}}%
+    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  [\textquotesingle Miosis\textquotesingle , \textquotesingle Anisocoria\textquotesingle ]\end{tabular}}}}%
+    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Cefalea\textquotesingle , \textquotesingle Sincope\textquotesingle , \textquotesingle Incontinencia\textquotesingle ]\end{tabular}}}}%
+    %to_fix
+
+    %Medicamentos (to_fix)
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesin...\end{tabular}}}}%
 
@@
     %Diabetes
-    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
-    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
-    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
+    \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
+    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg sdf sdfsd fsdf\end{tabular}}}}%
+    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     %Hipertension
-    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
-    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
-    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
+    \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
+    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdfsd sdf\end{tabular}}}}%
+    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    %Cardiopatias
+    \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
+    \put(0.63928128,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.59572153,0.48073243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No \end{tabular}}}}%        
+    %Neumopatias
+    \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
+    \put(0.63928128,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59572153,0.45747395){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    %Trauma
+    \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
+    \put(0.63928128,0.43527803){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59572153,0.43421546){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    %Alergy
+    \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
+    \put(0.63928128,0.41201958){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59572153,0.410957){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    %Other
+    \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
+    \put(0.63928128,0.38876109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %\put(0.59572153,0.38769855){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
 
+    %Exploracion Fisica
+    %Cabeza
+    \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
+    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rsa asdfg sdfgdfs gdf\end{tabular}}}}%
+    %Cara
+    \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
+    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg dfgdf gdfg\end{tabular}}}}%
+    %Cuello
+    \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
+    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Torax
+    \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
+    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.57421341,0.26602505){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Abdomen
+    \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
+    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.57421363,0.24991392){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Extremidades
+    \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
+    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.59031192,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Genitales
+    \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
+    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.58368309,0.21763312){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Columna
+    \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
+    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.58218801,0.19630385){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %Electro
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    %Signos Vitales 1
+    \put(0.48899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:31\end{tabular}}}}%
+    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
+    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 121\end{tabular}}}}%
+    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 122\end{tabular}}}}%
+    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 123\end{tabular}}}}%
+    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 124\end{tabular}}}}%
+    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 125\end{tabular}}}}%
+    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 126\end{tabular}}}}%
+    %Signos Vitales 2
+    \put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
+    \put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
+    \put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
+    \put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
+    \put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
+    \put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
+    \put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
+    \put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
   \end{picture}
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
-
-    \put(0.42638971,0.73960084){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%
-
-    %Paciente
-    \put(0.09655761,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
-    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62911649){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62796396){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 59\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lotzo Sanchez Jaime\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-
-    %Paciente desconocido
-    \put(0.01413581,0.52820903){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
-    \put(0.01376544,0.48794778){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
-    \put(0.01355075,0.45100148){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.11853319,0.43470284){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-
-    %Padecimiento
-    \put(0.02265882,0.24439213){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont se lastimo saltando del auto\end{tabular}}}}%
-
-    %Antecedentes
-    %Diabetes
-    \put(0.01071591,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes mellitus\end{tabular}}}}%
-    \put(0.1162418,0.15515692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si1 -\end{tabular}}}}%  
-    \put(0.14649555,0.15522432){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Diabetes melitus tipode evolucion y terapeutica actual\end{tabular}}}}%
-    %Hipertension
-    \put(0.01068221,0.14181276){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hipertension arterial\end{tabular}}}}%
-    \put(0.1162418,0.14066955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}- Si2 -\end{tabular}}}}%
-    \put(0.14662476,0.14188016){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}hipertension arterial tipode evolucion y terapeutica actual\end{tabular}}}}%
+    %Impresion diagnostica
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf sd\end{tabular}}}}%
+    %Tratamiento
+    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf sd\end{tabular}}}}%
+    %Derivacion
+    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont dalinde\end{tabular}}}}%
+    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Estable\end{tabular}}}}%
+    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el medico\end{tabular}}}}%
+    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
+    %Finalizacion
+    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfsd fsdfsd f\end{tabular}}}}%
+    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf\end{tabular}}}}%
+    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
+    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
+    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
+    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
+    \put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X1 }}\end{tabular}}}}%
+    \put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+    \put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
 

### 2022-08-17 ersteops/templates/printpdf/paperless_template.tex
clean no need packages
change fontface

@@
 %\usepackage{relsize}
-\usepackage{etoolbox}
+%\usepackage{etoolbox}
 \usepackage[paperwidth=27.94cm, paperheight=21.59cm, left=0.0cm,right=0.0cm,top=0.0in,bottom=0.0in,headheight=0in,headsep=0pt,footskip=120pt]{geometry}
@@
 %\usepackage{fancyhdr}
-\usepackage{uarial}
+%\usepackage{uarial}
 %\usepackage[scaled]{uarial}
 \usepackage{transparent}
-\usepackage[protrusion=true,expansion=true]{microtype}
-\usepackage{calc}
-\usepackage{verbatim}
-\makeatletter
-\g@addto@macro\@verbatim\small
-\makeatother 
+%\usepackage[protrusion=true,expansion=true]{microtype}
+%\usepackage{calc}
+%\usepackage{verbatim}
+%\makeatletter
+%\g@addto@macro\@verbatim\small
+%\makeatother 
 \usepackage{xcolor}
 
-\usepackage{lmodern}
+%\usepackage{lmodern}
 %\fontfamily{lmss}\selectfont
-\usepackage[utf8]{inputenc}
+%\usepackage[utf8]{inputenc}
 %\usepackage{unixode}
@@
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_pr}}\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_st}}\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qt}}\end{tabular}}}}%
-    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
-    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_pr}}\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_st}}\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_qt}}\end{tabular}}}}%
+    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
+    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
     %Signos Vitales 1

### 2022-08-17 ersteops/templates/printpdf/rendered_template.tex
clean no need packages
change fontface

@@
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%    
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%    
+    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA\end{tabular}}}}%
+    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{qcr}\selectfont NA \end{tabular}}}}%
     %Signos Vitales 1

### 2022-08-17 ersteops/templates/printpdf/paperless_template.tex
try tiny text

--- 2022-08-17 ersteops/templates/printpdf/paperless_template.tex
@@
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_rhythm}}\end{tabular}}}}%
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_frequency}}\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_p}}\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_pr}}\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_axis_qrs}}\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qrs}}\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_st}}\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_wave_t}}\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_qt}}\end{tabular}}}}%
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_rhythm}}\end{tabular}}}}%
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_frequency}}\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_p}}\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_pr}}\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_axis_qrs}}\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qrs}}\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_st}}\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_t}}\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qt}}\end{tabular}}}}%
     \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%

### 2022-08-17 ersteops/templates/printpdf/rendered_template.tex
try tiny text

--- 2022-08-17 ersteops/templates/printpdf/rendered_template.tex
@@
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%    
     \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

### 2022-08-18 ersteops/paperless/views.py
fix logic

@@ -265,14 +265,14 @@ def new_medicalreport(request):
           airway= vue_data['airway'],
           other_airway= vue_data['other_airway'], 
           physical_exploration= vue_data['physical_exploration'], 
-          normal_head= find_on_list(vue_data['normal_elements'],'Cabeza'), 
-          normal_face= find_on_list(vue_data['normal_elements'],'Cara'), 
-          normal_neck= find_on_list(vue_data['normal_elements'],'Cuello'), 
-          normal_torax= find_on_list(vue_data['normal_elements'],'Tórax'), 
-          normal_abdomen= find_on_list(vue_data['normal_elements'],'Abdomen'), 
-          normal_limbs= find_on_list(vue_data['normal_elements'],'Extremidades'), 
-          normal_genitals= find_on_list(vue_data['normal_elements'],'Genitales'), 
-          normal_spine= find_on_list(vue_data['normal_elements'],'Columna Vertebral'), 
+          normal_head= not_find_on_list(vue_data['normal_elements'],'Cabeza'), 
+          normal_face= not_find_on_list(vue_data['normal_elements'],'Cara'), 
+          normal_neck= not_find_on_list(vue_data['normal_elements'],'Cuello'), 
+          normal_torax= not_find_on_list(vue_data['normal_elements'],'Tórax'), 
+          normal_abdomen= not_find_on_list(vue_data['normal_elements'],'Abdomen'), 
+          normal_limbs= not_find_on_list(vue_data['normal_elements'],'Extremidades'), 
+          normal_genitals= not_find_on_list(vue_data['normal_elements'],'Genitales'), 
+          normal_spine= not_find_on_list(vue_data['normal_elements'],'Columna Vertebral'), 
           current_condition= vue_data['current_condition'], 
           pupil_state_left= vue_data['pupil_state_left'], 
           pupil_state_right= vue_data['pupil_state_right'], 
@@ -367,6 +367,13 @@ def find_on_list(my_list_Dict, what_to_search):
   my_text='No'
   if my_list_Dict.count(what_to_search) > 0:
     my_text = 'Si'
+  return my_text
+
+def not_find_on_list(my_list_Dict, what_to_search):
+  #define Yes or No if key is on dict
+  my_text='Si'
+  if my_list_Dict.count(what_to_search) > 0:
+    my_text = 'No'
   return my_text
 
 

### 2022-08-18 ersteops/printpdf/views.py
add function to split line every n characters

@@ -188,6 +188,7 @@ def generate_tex(params,output_mode):
     return True
     return False
 
+
 def escape_params(params):
   escaped_params = {}
   for k,v in params.items():
@@ -286,8 +287,36 @@ def escape_text(s):
 def get_medical_report(pk):
   #medical_Report = MedicalReport.get(id=pk)
   medical_Report = MedicalReport.objects.filter(id=pk).values()[0]
-  
+  raw_medical_Report = MedicalReport.objects.get(id=pk)
+  medical_Report['json_physical_exploration'] = list(eval(raw_medical_Report.physical_exploration))
+  medical_Report['json_medications'] = list(eval(raw_medical_Report.medications))
+  medical_Report['json_airway'] = list(eval(raw_medical_Report.airway)) 
+  medical_Report['json_consultation_reason'] = list(eval(raw_medical_Report.consultation_reason))
+  medical_Report['json_pupil_state_left'] = list(eval(raw_medical_Report.pupil_state_left))
+  medical_Report['json_pupil_state_right'] = list(eval(raw_medical_Report.pupil_state_right))
+  medical_Report['json_traumatics'] = list(eval(raw_medical_Report.traumatics))    
+  medical_Report['json_inmovilization_type'] = list(eval(raw_medical_Report.inmovilization_type))
+  medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,67)
+  medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,67)
+  medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,67)  
 
   return medical_Report
 
 
+def add_line_breaks(break_string,every):
+  #res = '\n '.join(a + b for a, b in zip(break_string[::3], break_string[1::3]))
+  #return res
+  # initializing K
+  K = '\n'
+ 
+  # initializing N
+  N = every
+ 
+  x=list(break_string)
+  ns=""
+  for i in range(0,len(x)):
+    if(i!=0 and i%N==0):
+        ns+=K
+    else:
+        ns+=break_string[i]
+  return ns

### 2022-08-18 ersteops/templates/printpdf/paperless_template.tex
update templates

@@
 
+    %Folio
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.id}}\end{tabular}}}}%
+
     \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
@@
     %Padecimiento
-    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
+    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_current_condition}}\end{tabular}}}}%
     %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
@@
     \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.event_type}} \end{tabular}}}}%
-    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.traumatics}} \end{tabular}}}}%
-    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo:{{content.pupil_state_left}}\end{tabular}}}}%
-    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {{content.pupil_state_right}}\end{tabular}}}}%
-    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.consultation_reason}}\end{tabular}}}}%
+    %Trauma
+    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_traumatics %}{{ item }},{% endfor %}\end{tabular}}}}%
+    %Ojo Izquierdo
+    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
+    %Ojo Derecho
+    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
+    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_consultation_reason %}{{ item }},{% endfor%}
+    \end{tabular}}}}%
     %to_fix
+    %Via Aerea
+    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{% for item in content.json_airway %}\fontfamily{lmss}\selectfont\scriptsize {{ item.airway_type}} - {{ item.instruction }}\\{% endfor %}\end{tabular}}}}%
 
     %Medicamentos (to_fix)
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ content.medications|truncatechars:20}}\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ content.medications }}\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
+    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_medications %}{{ item.medication_type }} - {{ item.medication_name }} - {{ item.medication_hrs }} hrs\\{% endfor %}\end{tabular}}}}%
 
@@
     \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
-    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
+    %\put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
     %Signos Vitales 1
-    \put(0.48899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:31\end{tabular}}}}%
-    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
-    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 121\end{tabular}}}}%
-    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 122\end{tabular}}}}%
-    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 123\end{tabular}}}}%
-    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 124\end{tabular}}}}%
-    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 125\end{tabular}}}}%
-    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 126\end{tabular}}}}%
+    {% for item in content.json_physical_exploration%}
+    \put(0.47899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.time }}\end{tabular}}}}%
+    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.heart_rate }}\end{tabular}}}}%
+    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.respiratory_rate}}\end{tabular}}}}%
+    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.blood_pressure}}\end{tabular}}}}%
+    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.temperature}}\end{tabular}}}}%
+    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.oxygen_saturation}}\end{tabular}}}}%
+    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.glucometry}}\end{tabular}}}}%
+    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.glassgow_total }}\end{tabular}}}}%
+    {% endfor %}
     %Signos Vitales 2
-    \put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
-    \put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
-    \put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
-    \put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
-    \put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
-    \put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
-    \put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
-    \put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
+    %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
+    %\put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
+    %\put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
+    %\put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
+    %\put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
+    %\put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
+    %\put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
+    %\put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
   \end{picture}
@@
     %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.treatment}}\end{tabular}}}}%
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
     %Tratamiento
-    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.diagnostic_impresion}}\end{tabular}}}}%
+    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_treatment}} \end{tabular}}}}%
     %Derivacion
@@
     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_operator}}\end{tabular}}}}%
-    \put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X1 }}\end{tabular}}}}%
-    \put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-    \put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ {{ content.demarcation_responsable }} }}\end{tabular}}}}%
+    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%

### 2022-08-18 ersteops/templates/printpdf/rendered_template.tex
update templates

@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 34
+    %    \textbf{Consulta \#:} 40
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf34
+    %    \textbf40
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 34
+%     %    \textbf{Consulta \#:} 40
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 34 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 34 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 40 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 40 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-001 }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-002 }\end{tabular}}}}%
 
@@
 
+    %Folio
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 40\end{tabular}}}}%
+
     \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
     \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-001\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-002\end{tabular}}}}%
 
@@
     \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 45\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Nika Sanchez Jaime\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont luiis spota\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5\end{tabular}}}}%
+    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont paciente desconocido y asi\end{tabular}}}}%
-    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  la filiacion desconocida\end{tabular}}}}%
-    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont pantalon rojo rotio\end{tabular}}}}%
-    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rojo rojo amarillo\end{tabular}}}}%
+    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
+    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%
-    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdf sdfsdf sdf sdfsd fsd\end{tabular}}}}%
+    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl \\asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle af \\ nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle aff nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%
 
     %Generales
-    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hogar \end{tabular}}}}%
-    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Urgencias \end{tabular}}}}%
-    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Traumaticos \end{tabular}}}}%
-    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Craneal\textquotesingle , \textquotesingle Craneoencefalico\textquotesingle ] \end{tabular}}}}%
-    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo:[\textquotesingle Isocoria\textquotesingle , \textquotesingle Midriasis\textquotesingle ]\end{tabular}}}}%
-    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  [\textquotesingle Miosis\textquotesingle , \textquotesingle Anisocoria\textquotesingle ]\end{tabular}}}}%
-    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\textquotesingle Cefalea\textquotesingle , \textquotesingle Sincope\textquotesingle , \textquotesingle Incontinencia\textquotesingle ]\end{tabular}}}}%
+    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    %Trauma
+    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    %Ojo Izquierdo
+    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: \end{tabular}}}}%
+    %Ojo Derecho
+    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  \end{tabular}}}}%
+    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 
+    \end{tabular}}}}%
     %to_fix
+    %Via Aerea
+    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
 
     %Medicamentos (to_fix)
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesin...\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
+    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
 
@@
     \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg sdf sdfsd fsdf\end{tabular}}}}%
-    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
     %Hipertension
     \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
-    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdfsd sdf\end{tabular}}}}%
-    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
     %Cardiopatias
@@
     \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont rsa asdfg sdfgdfs gdf\end{tabular}}}}%
+    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
     %Cara
@@
     \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfg dfgdf gdfg\end{tabular}}}}%
+    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
     %Cuello
     \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
-    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
-    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.57421341,0.26602505){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
-    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.57421363,0.24991392){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
-    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.59031192,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
-    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.58368309,0.21763312){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
-    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
     \put(0.58218801,0.19630385){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    %\put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA []\end{tabular}}}}%
     %Signos Vitales 1
-    \put(0.48899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:31\end{tabular}}}}%
-    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
-    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 121\end{tabular}}}}%
-    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 122\end{tabular}}}}%
-    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 123\end{tabular}}}}%
-    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 124\end{tabular}}}}%
-    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 125\end{tabular}}}}%
-    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 126\end{tabular}}}}%
+
     %Signos Vitales 2
-    \put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
-    \put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
-    \put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
-    \put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
-    \put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
-    \put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
-    \put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
-    \put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
+    %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
+    %\put(0.56346295,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 220\end{tabular}}}}%
+    %\put(0.62325414,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 321\end{tabular}}}}%
+    %\put(0.68836013,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 422\end{tabular}}}}%
+    %\put(0.74651878,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 523\end{tabular}}}}%
+    %\put(0.81241818,0.59432876){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 624\end{tabular}}}}%
+    %\put(0.87214411,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 725\end{tabular}}}}%
+    %\put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
   \end{picture}
@@
     %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf sd\end{tabular}}}}%
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
     %Tratamiento
-    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf sd\end{tabular}}}}%
+    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
     %Derivacion
-    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont dalinde\end{tabular}}}}%
-    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Estable\end{tabular}}}}%
-    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el medico\end{tabular}}}}%
-    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
+    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
+    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
     %Finalizacion
-    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sdfsd fsdfsd f\end{tabular}}}}%
-    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont sd fsdf sdf\end{tabular}}}}%
+    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
@@
     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
-    \put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X1 }}\end{tabular}}}}%
-    \put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-    \put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
+    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%

### 2022-08-18 ersteops/paperless/dict_fields.py
update dict

@@ -93,4 +93,6 @@ MedicalReportDict = {
 "crew_medic_id_card":"",
 "crew_tum":"",
 "crew_operator":"",
+"signature_client":"",
+"signature_medic":"",
 }

### 2022-08-18 ersteops/paperless/models.py
add signature field

@@ -219,7 +219,7 @@ class MedicalReport(models.Model):
     crew_tum = models.CharField("TUM",blank=True,default='',max_length=50)
     crew_operator = models.CharField("Operador",blank=True,default='',max_length=50) 
     final_report = models.FileField("archivo de estudios(pdf o jpg)",validators=[FileExtensionValidator(allowed_extensions=['pdf','jpg'])],max_length=100,upload_to="pdffile/pdf_files",default="",blank=True)
-
+    signature_client = models.TextField('Signature Client',blank=True)
 
     def json_physical_exploration(self):
         #convert_to_json

### 2022-08-18 ersteops/paperless/views.py
add logic for signature

@@ -232,6 +232,7 @@ def new_medicalreport(request):
           logger.info('[ NEW MEWDICAL REPORT DATA: -5- {} ]'.format(data['paperless']))
           vue_data=json.loads(data['paperless'])
           logger.info('[ NEW MEWDICAL REPORT DATA: -6- {} ]'.format(vue_data['service_code']))
+          logger.info('[ NEW MEWDICAL REPORT DATA: -7- {} ]'.format(vue_data['signature_client']))
           qs = Emergency.objects.get(id=vue_data['service_code'])
           medicalReport = MedicalReport.objects.create(
           odoo_client = qs.odoo_client,
@@ -338,8 +339,10 @@ def new_medicalreport(request):
           crew_medic_id_card = vue_data['crew_medic_id_card'],
           crew_tum = vue_data['crew_tum'],
           crew_operator = vue_data['crew_operator'],
+          signature_client = vue_data['signature_client'],
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
+
           Send_Mail_To(request,vue_data['email'],medicalReport.id)
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
           pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
@@ -355,6 +358,7 @@ def new_medicalreport(request):
       except Exception as e:
           logger.error("[Create Medical Report View ERROR]: {}, type: {}".format(e, type(e)))
           return bad_response
+
       #qs.medical_report = medicalReport
       #qs.save()
 

### 2022-08-18 ersteops/printpdf/views.py
add function to extract signatur from databasea end generate png

@@ -29,6 +29,7 @@ from paperless.models import MedicalReport
 import logging
 logger = logging.getLogger('django_info')
 
+import base64
 
 
 # Create your views here.
@@ -171,7 +172,7 @@ def generate_tex(params,output_mode):
            'latex_overpic_foot':latex_overpic_foot,
            'latex_graphics_path':latex_graphics_path,
        }
-  logger.info('[ PRINTPDF! - context {}]'.format(context)) 
+  #logger.info('[ PRINTPDF! - context {}]'.format(context)) 
   # Render template
   rendered_tpl = template.render(context).encode('utf-8')
   # Write Template to file
@@ -299,8 +300,35 @@ def get_medical_report(pk):
   medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,67)
   medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,67)
   medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,67)  
-
+  medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   return medical_Report
+
+def save_png(target_file,data_uri):
+  have_signature_file = True
+  if data_uri:
+    encoded_data = data_uri.split(",")
+    encoded_image = encoded_data[1]
+    res = bytes(encoded_image, 'utf-8')
+    logger.info('[ PRINTPDF! - signature to png encode -------------- ]')
+    png_recovered = base64.decodestring(res)
+    logger.info('[ PRINTPDF! - signature to png process {}]'.format(encoded_image))  
+    try:
+      f = open(settings.BASE_DIR+'/templates/printpdf/{}.png'.format(target_file),'wb')
+      f.write(png_recovered)
+      f.close
+      logger.info('[ PRINTPDF! - signature to png succesfull]')
+
+    except Exception as e:
+      logger.error('[ PRINTPDF! - signature ERROR]')
+      logger.error(e)
+      have_signature_file = False
+  else:
+    have_signature_file = False
+  return have_signature_file
+
+  #decoded_image = Base64.decode64(encoded_image)
+  #File.open("signature.png", "wb") { |f| f.write(decoded_image) }
+
 
 
 def add_line_breaks(break_string,every):

### 2022-08-18 frontend/components/SignatureClient/script.js
add save from frontend

@@ -32,6 +32,9 @@ export default {
   //   components: {
   //   VueSignaturePad
   // },
+  data: () => ({
+    paperless: window.erste.paperless,
+  }),
   methods: {
     async undo(e) {
       e.preventDefault();
@@ -45,6 +48,9 @@ export default {
       const { isEmpty, data } = this.$refs.signaturePad.saveSignature();
       console.log(isEmpty);
       console.log(data);
+      this.paperless.signature_client = data;
+      console.log(this.paperless.signature_client);
+      alert(`Firma almacenada${this.paperless.signature_client}`);
     },
   },
 };

### 2022-08-18 ersteops/templates/printpdf/rendered_template.tex
update template

@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 40
+    %    \textbf{Consulta \#:} 46
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf40
+    %    \textbf46
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 40
+%     %    \textbf{Consulta \#:} 46
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 40 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 40 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 46 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 46 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
 %     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-002 }\end{tabular}}}}%
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
+    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
+    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
 
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 40\end{tabular}}}}%
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 46\end{tabular}}}}%
 
@@
     \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
     \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-002\end{tabular}}}}%
@@
     \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5\end{tabular}}}}%
+    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 0\end{tabular}}}}%
     \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
@@
     %Padecimiento
-    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl \\asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle af \\ nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%
-    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el padecimiento actual \\fasd dasf asdklfnadskl; fn;klasdnfkl asdnfklsdnklf nsdklfn dklsnfklsdnf klsdnf klsdnf lksdnklf asdkl\textquotesingle aff nsdklfgn mklsdfnm l;sdknf lksdnfklsdnf lksdn\end{tabular}}}}%
+    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 
@@
     \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asdasdasd asd\end{tabular}}}}%
     %Cara
     \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont gh jkhugjjkgh\end{tabular}}}}%
     %Cuello
     \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
-    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
+    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont qweqwe\end{tabular}}}}%
     %Torax
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
+    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
     %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont dfhgh dfgdfg df\end{tabular}}}}%
     %Tratamiento
-    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asdasf sdg fdg df \end{tabular}}}}%
     %Derivacion

### 2022-08-19 ersteops/templates/printpdf/paperless_template.tex
update template
add medic signature

@@
 \usepackage{xcolor}
+
+\usepackage[export]{adjustbox}
 
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
+    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
+    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
 
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
+    {% if content.have_client_signature %}
+    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+    {% endif %}
+    {% if content.have_medic_signature %}
+    \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
+    \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+    {% endif %}
     %Impresion diagnostica
@@
     %Finalizacion
-    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%\
+
     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_relation}}\end{tabular}}}}%

### 2022-08-19 ersteops/templates/printpdf/rendered_template.tex
add medic signature

--- 2022-08-18 ersteops/templates/printpdf/rendered_template.tex
@@
 
+\usepackage[export]{adjustbox}
+
 %\usepackage{lmodern}
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 40
+    %    \textbf{Consulta \#:} 49
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf40
+    %    \textbf49
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 40
+%     %    \textbf{Consulta \#:} 49
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 40 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 40 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 49 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 49 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-002 }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-006 }\end{tabular}}}}%
 
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
+    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
+    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
 
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 40\end{tabular}}}}%
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 49\end{tabular}}}}%
 
@@
     \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-002\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-006\end{tabular}}}}%
 
@@
     \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
+
+    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+
+    \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
+    \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+
     %Impresion diagnostica
@@
     %Finalizacion
-    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\
+
     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

### 2022-08-19 ersteops/paperless/models.py

@@ -220,6 +220,7 @@ class MedicalReport(models.Model):
     crew_operator = models.CharField("Operador",blank=True,default='',max_length=50) 
     final_report = models.FileField("archivo de estudios(pdf o jpg)",validators=[FileExtensionValidator(allowed_extensions=['pdf','jpg'])],max_length=100,upload_to="pdffile/pdf_files",default="",blank=True)
     signature_client = models.TextField('Signature Client',blank=True)
+    signature_medic = models.TextField('Signature Medic',blank=True)
 
     def json_physical_exploration(self):
         #convert_to_json

### 2022-08-19 ersteops/paperless/views.py

@@ -340,6 +340,7 @@ def new_medicalreport(request):
           crew_tum = vue_data['crew_tum'],
           crew_operator = vue_data['crew_operator'],
           signature_client = vue_data['signature_client'],
+          signature_medic = vue_data['signature_medic'],
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
 

### 2022-08-19 ersteops/printpdf/views.py

@@ -301,6 +301,7 @@ def get_medical_report(pk):
   medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,67)
   medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,67)  
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
+  medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)  
   return medical_Report
 
 def save_png(target_file,data_uri):

### 2022-08-19 frontend/components/MedicalReport/script.js

@@ -2,6 +2,7 @@ import 'filters/time-since';
 import AirWay from 'components/AirWay';
 import PhysicalExploration from 'components/PhysicalExploration';
 import SignatureClient from 'components/SignatureClient';
+import SignatureMedic from 'components/SignatureMedic';
 import Medications from 'components/Medications';
 import { mapActions } from 'vuex';
 // import GoogleMap from './components/GoogleMap.vue'
@@ -44,7 +45,13 @@ export default {
     // const canvas = document.querySelector("canvas");
     // const signaturePad = new SignaturePad(canvas);
   }),
-  components: { AirWay, PhysicalExploration, SignatureClient, Medications },
+  components: {
+    AirWay,
+    PhysicalExploration,
+    SignatureClient,
+    SignatureMedic,
+    Medications,
+  },
   methods: {
     ...mapActions('newMedicalReport', ['createMedicalReport']),
 

### 2022-08-19 frontend/components/SignatureMedic/script.js

@@ -1,0 +1,56 @@
+// import { VueSignaturePad } from 'vue-signature-pad';
+
+export default {
+  name: 'SignatureMedic',
+  // data: () => ({
+  //   options: {
+  //     penColor: "#c0f",
+  //   },
+  // }),
+  // methods: {
+  //   undo() {
+  //     this.$refs.signaturePad.undoSignature();
+  //   },
+  //   save() {
+  //     const { isEmpty, data } = this.$refs.signaturePad.saveSignature();
+
+  //     alert("Open DevTools see the save data.");
+  //     console.log(isEmpty);
+  //     console.log(data);
+  //   },
+  //   change() {
+  //     this.options = {
+  //       penColor: "#00f",
+  //     };
+  //   },
+  //   resume() {
+  //     this.options = {
+  //       penColor: "#c0f",
+  //     };
+  //   },
+  // },
+  //   components: {
+  //   VueSignaturePad
+  // },
+  data: () => ({
+    paperless: window.erste.paperless,
+  }),
+  methods: {
+    async undo(e) {
+      e.preventDefault();
+      e.stopPropagation();
+      this.$refs.signaturePad.undoSignature();
+    },
+    async save(e) {
+      e.preventDefault();
+      e.stopPropagation();
+
+      const { isEmpty, data } = this.$refs.signaturePad.saveSignature();
+      console.log(isEmpty);
+      console.log(data);
+      this.paperless.signature_medic = data;
+      console.log(this.paperless.signature_medic);
+      alert(`Firma almacenada${this.paperless.signature_medic}`);
+    },
+  },
+};

### 2022-08-19 ersteops/templates/printpdf/paperless_template.tex
add sendmail logic and signature for privacy statment

@@
     {% if content.have_client_signature %}
-    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
+    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
     {% endif %}

### 2022-08-19 ersteops/templates/printpdf/rendered_template.tex
add sendmail logic and signature for privacy statment

@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 49
+    %    \textbf{Consulta \#:} 51
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf49
+    %    \textbf51
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 49
+%     %    \textbf{Consulta \#:} 51
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 49 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 49 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 51 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 51 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
@@
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 49\end{tabular}}}}%
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 51\end{tabular}}}}%
 
@@
     \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Femenino\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5\end{tabular}}}}%
+    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 14\end{tabular}}}}%
     \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
@@
 
-    \put(0.78960956,0.16450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
+    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 

### 2022-08-19 ersteops/paperless/views.py

@@ -343,8 +343,7 @@ def new_medicalreport(request):
           signature_medic = vue_data['signature_medic'],
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
-
-          Send_Mail_To(request,vue_data['email'],medicalReport.id)
+          Send_Mail_To(request,vue_data['email'],medicalReport.id,vue_data['send_email'])
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
           pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
           pdf = pdf_file.read()
@@ -382,7 +381,7 @@ def not_find_on_list(my_list_Dict, what_to_search):
   return my_text
 
 
-def Send_Mail_To(request,email_recive,pk):
+def Send_Mail_To(request,email_recive,pk,send_flag):
   #Send mail via smtp gmail server
   try:
     email = EmailMessage(
@@ -399,8 +398,8 @@ def Send_Mail_To(request,email_recive,pk):
     email.attach(file_name,pdf,'application/pdf')
     #pdf_to_attach = os.path.join(tempdir, 'rendered_template.pdf')
     #email.attach_file(pdf_to_attach)
-
-    email.send()
+    if send_flag:
+      email.send()
     logger.info('[ NEW MEWDICAL SendMail : {} ]'.format(email_recive))
   except Exception as e:
     logger.error("[Create Medical Report Email ERROR]: {}, type: {}".format(e, type(e)))

### 2022-08-19 ersteops/templates/printpdf/rendered_template.tex
change button label

@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 51
+    %    \textbf{Consulta \#:} 52
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf51
+    %    \textbf52
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 51
+%     %    \textbf{Consulta \#:} 52
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 51 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 51 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 52 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 52 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-006 }\end{tabular}}}}%
+%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ SOPORTE }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
 
@@
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 51\end{tabular}}}}%
+    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 52\end{tabular}}}}%
 
@@
     \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-006\end{tabular}}}}%
+   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont SOPORTE\end{tabular}}}}%
+    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-005\end{tabular}}}}%
 
@@
     \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 14\end{tabular}}}}%
+    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 21\end{tabular}}}}%
     \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
@@
     %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont busca el bug!\end{tabular}}}}%
     %Tratamiento

### 2022-08-19 frontend/components/SignatureClient/script.js

@@ -50,7 +50,7 @@ export default {
       console.log(data);
       this.paperless.signature_client = data;
       console.log(this.paperless.signature_client);
-      alert(`Firma almacenada${this.paperless.signature_client}`);
+      // alert(`Firma almacenada${this.paperless.signature_client}`);
     },
   },
 };

### 2022-08-19 frontend/components/SignatureMedic/script.js

@@ -50,7 +50,7 @@ export default {
       console.log(data);
       this.paperless.signature_medic = data;
       console.log(this.paperless.signature_medic);
-      alert(`Firma almacenada${this.paperless.signature_medic}`);
+      // alert(`Firma almacenada${this.paperless.signature_medic}`);
     },
   },
 };

### 2022-08-24 ersteops/paperless/dict_fields.py
change type

@@ -65,7 +65,7 @@ MedicalReportDict = {
 "electro_interpretation": "",
 "derivation_amount": "",
 "derivation_recive": "",
-"derivation_type": [],
+"derivation_type": "",
 "demarcation_responsable": "",
 "demarcation_relation": "",
 "electro_qrs":"",

### 2022-08-24 ersteops/paperless/migrations/0033_medicalreport_odoo_client_data.py
update model field sizes

@@ -1,0 +1,18 @@
+# Generated by Django 2.2.27 on 2022-08-22 20:54
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('paperless', '0032_medicalreport_signature_medic'),
+    ]
+
+    operations = [
+        migrations.AddField(
+            model_name='medicalreport',
+            name='odoo_client_data',
+            field=models.CharField(blank=True, default='', max_length=120, verbose_name='Socio'),
+        ),
+    ]

### 2022-08-24 ersteops/paperless/migrations/0034_auto_20220823_0323.py

@@ -1,0 +1,22 @@
+# Generated by Django 2.2.27 on 2022-08-23 03:23
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('paperless', '0033_medicalreport_odoo_client_data'),
+    ]
+
+    operations = [
+        migrations.RemoveField(
+            model_name='medicalreport',
+            name='odoo_client_data',
+        ),
+        migrations.AddField(
+            model_name='medicalreport',
+            name='odoo_client_name',
+            field=models.CharField(blank=True, default='', max_length=200, verbose_name='Socio'),
+        ),
+    ]

### 2022-08-24 ersteops/paperless/migrations/0035_auto_20220824_0237.py

@@ -1,0 +1,98 @@
+# Generated by Django 2.2.27 on 2022-08-24 02:37
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('paperless', '0034_auto_20220823_0323'),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='demarcation_relation',
+            field=models.CharField(blank=True, default=False, max_length=20, verbose_name='Deslinde relacion'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='demarcation_responsable',
+            field=models.CharField(blank=True, default=False, max_length=50, verbose_name='Deslinde responsable'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_abnormalities',
+            field=models.TextField(blank=True, default='', max_length=100, verbose_name='Anormalidades'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_axis_qrs',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='Eje QRS'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_frequency',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='Frecuencia'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_pr',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='PR'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_qt',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='QT'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_rhythm',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='Ritmo'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_st',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='ST'),
+        ),
+        migrations.AlterField(
+            model_name='medicalreport',
+            name='electro_wave_p',
+            field=models.CharField(blank=True, default='', max_length=50, verbose_name='Onda P'),
+        ),
+        migrations.AlterField(
[…]

### 2022-08-24 ersteops/paperless/models.py

@@ -95,6 +95,7 @@ class MedicalReport(models.Model):
         )
     odoo_client = models.CharField("Cliente id(Legacy)", max_length=50,default ='',)
     erste_code = models.CharField("ID Code", max_length=50, blank=True, default="")
+    odoo_client_name = models.CharField("Socio", max_length=200,blank=True, default="")
     service_code = models.CharField("Codigo de Servicio",max_length=10,default='')
     service_unit = models.CharField("Unidad Movil",max_length=10,default='')
     service_unit_type = models.CharField("Tipo Unidad",max_length=50,default='')
@@ -109,22 +110,22 @@ class MedicalReport(models.Model):
     patient_name = models.CharField('Nombre del Paciente', max_length=255, default='')
     patient_gender = models.CharField('genero', max_length=15, default= '', blank=True, choices=GENDER)
     patient_age = models.IntegerField('edad (años)', default=0, blank=True)
-    patient_address = models.CharField('Direccion', max_length=50, default='', blank=False)
-    patient_affiliations = models.CharField("Filiacion",max_length=50,blank=True)
+    patient_address = models.CharField('Direccion', max_length=150, default='', blank=False)
+    patient_affiliations = models.CharField("Filiacion",max_length=150,blank=True)
     is_patient_unknow = models.CharField("Es paciente desconocido",max_length=50,blank=True,default='')
     patient_unknow = models.CharField("Paciente Desconocido",max_length=50,blank=True)
     patient_clothes = models.CharField("Vestimenta", max_length=50,blank=True)
     patient_phone = models.CharField("Telefono:", max_length=15,blank=True ,default='')
     attention_place = models.CharField('Sitio de Atencion', max_length=20, default= '', blank=True, choices=ATENTION_PLACE)
     other_attention_place = models.CharField('Otro Sitio de Atencion', max_length=20, default= '', blank=True, choices=ATENTION_PLACE)
-    skin_color = models.CharField("Coloración de piel", max_length=50, default= '', blank=True,)
+    skin_color = models.CharField("Coloración de piel", max_length=150, default= '', blank=True,)
     service_type = models.CharField('Tipo de Servicio', max_length=50, default= '', blank=True, choices=SERVICE_TYPE)
     other_service_type = models.CharField('Tipo de Servicio', max_length=50, default= '', blank=True)
[…]

### 2022-08-24 ersteops/paperless/views.py
add field an messages

@@ -341,8 +341,10 @@ def new_medicalreport(request):
           crew_operator = vue_data['crew_operator'],
           signature_client = vue_data['signature_client'],
           signature_medic = vue_data['signature_medic'],
+          odoo_client_name = qs.partner_name,
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
+          messages.info(request, "Parte Medico Sending email an generating pdf!!!")
           Send_Mail_To(request,vue_data['email'],medicalReport.id,vue_data['send_email'])
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
           pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')

### 2022-08-24 ersteops/printpdf/views.py
add emergency data

@@ -24,7 +24,7 @@ import os.path
 
 from paperless.dict_fields import MedicalReportDict
 from paperless.models import MedicalReport
-
+from emergency.models import Emergency
 # Logging library
 import logging
 logger = logging.getLogger('django_info')
@@ -289,6 +289,7 @@ def get_medical_report(pk):
   #medical_Report = MedicalReport.get(id=pk)
   medical_Report = MedicalReport.objects.filter(id=pk).values()[0]
   raw_medical_Report = MedicalReport.objects.get(id=pk)
+  emergency = Emergency.objects.get(id=raw_medical_Report.service_code)
   medical_Report['json_physical_exploration'] = list(eval(raw_medical_Report.physical_exploration))
   medical_Report['json_medications'] = list(eval(raw_medical_Report.medications))
   medical_Report['json_airway'] = list(eval(raw_medical_Report.airway)) 
@@ -298,10 +299,17 @@ def get_medical_report(pk):
   medical_Report['json_traumatics'] = list(eval(raw_medical_Report.traumatics))    
   medical_Report['json_inmovilization_type'] = list(eval(raw_medical_Report.inmovilization_type))
   medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,67)
-  medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,67)
-  medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,67)  
+  medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,41)
+  medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,41)  
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
-  medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)  
+  medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
+  medical_Report['emergency_created_at'] = emergency.created_at.strftime('%Y-%m-%d')
+  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.strftime('%H:%M')
+  medical_Report['arrival_time'] = emergency.arrival_time.strftime('%H:%M')
[…]

### 2022-08-24 ersteops/templates/printpdf/paperless_template.tex
update template

--- 2022-08-18 ersteops/templates/printpdf/paperless_template.tex
@@
     \setlength\tabcolsep{0pt}%
-    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
+    \put(0,0){\includegraphics[width=\unitlength,page=1]{master_parte_medico}}%
+    %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
+    %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
+    %Times
+    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.emergency_created_at}}\end{tabular}}}}%
+    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.unit_dispatched_time}}\end{tabular}}}}%
+    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.arrival_time}}\end{tabular}}}}%
+    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.attention_time}}\end{tabular}}}}%
+    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.final_emergency_time}}\end{tabular}}}}%
 
+    {% if content.attention_final_grade == 'G0' %}
+    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+    {% endif %}
+    {% if content.attention_final_grade == 'G1' %}
+    \put(0.42545332,0.57475133){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+    {% endif %}
+    {% if content.attention_final_grade == 'G2' %}
+    \put(0.4811341,0.5742217){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+    {% endif %}
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.id}}\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.id}}\end{tabular}}}}%
 
-    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_code}}\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit}}\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_type}}\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_unit_plate}}\end{tabular}}}}%
+    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_code}}\end{tabular}}}}%
+    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit}}\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_type}}\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_plate}}\end{tabular}}}}%
 
     %Paciente
-    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.erste_code}}\end{tabular}}}}%
-    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_phone}}\end{tabular}}}}%
-    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_gender}}\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_age}}\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_name}}\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_address}}\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.erste_code}} - {{content.odoo_client_name}}\end{tabular}}}}%
+    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_phone}}\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_gender}}\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_age}}\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_name}}\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_address}}\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_unknow}}\end{tabular}}}}%
-    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  {{content.patient_affiliations}}\end{tabular}}}}%
-    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.patient_clothes}}\end{tabular}}}}%
-    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.skin_color}}\end{tabular}}}}%
+    \put(0.23723674,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_unknow}}\end{tabular}}}}%
+    \put(0.07146203,0.50540156){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  {{content.patient_affiliations}}\end{tabular}}}}%
+    \put(0.07920229,0.49404644){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_clothes}}\end{tabular}}}}%
+    \put(0.37437746,0.49499384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.skin_color}}\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_current_condition}}\end{tabular}}}}%
+    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_current_condition}}\end{tabular}}}}%
     %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.current_condition}}\end{tabular}}}}%
@@
     %Generales
-    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.attention_place}} \end{tabular}}}}%
-    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.service_type}} \end{tabular}}}}%
-    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.event_type}} \end{tabular}}}}%
+    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.attention_place}} \end{tabular}}}}%
+    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_type}} \end{tabular}}}}%
+    {% if content.event_type == 'Traumaticos'%}
+      \put(0.30180123,0.46556814){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
+    {% else %}
+      \put(0.3007691,0.47620579){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
+    {% endif%}
     %Trauma
-    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_traumatics %}{{ item }},{% endfor %}\end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_traumatics %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor %}\end{tabular}}}}%
     %Ojo Izquierdo
-    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
+    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
     %Ojo Derecho
-    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
-    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_consultation_reason %}{{ item }},{% endfor%}
+    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_consultation_reason %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
     \end{tabular}}}}%
@@
     %Via Aerea
-    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{% for item in content.json_airway %}\fontfamily{lmss}\selectfont\scriptsize {{ item.airway_type}} - {{ item.instruction }}\\{% endfor %}\end{tabular}}}}%
+    \put(0.32505266,0.47551987){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{% for item in content.json_airway %}\fontfamily{lmss}\selectfont\scriptsize {{ item.airway_type}} - {{ item.instruction }}\\{% endfor %}\end{tabular}}}}%
+
+    {% for item in content.json_pupil_state_left%}
+      {% if item == 'Isocoria'%}
+        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Midriasis'%}
+        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Miosis'%}
+        \put(0.4335137,0.38189188){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Anisocoria'%}    
+        \put(0.43399571,0.35447078){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+    {% for item in content.json_pupil_state_right %}
+      {% if item == 'Isocoria'%}
+        \put(0.45563683,0.44651401){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Midriasis'%}
+        \put(0.45601685,0.41487724){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Miosis'%}
+        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+      {% if item == 'Anisocoria'%}  
+        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+      {% endif %}
+    {% endfor%}
+
+    %inmovilizacion
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}{% for item in content.json_inmovilization_type %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
+    \end{tabular}}}}%
+
+    %Impresion diagnostica
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
+    %Tratamiento
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%
 
@@
     %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
-    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_medications %}{{ item.medication_type }} - {{ item.medication_name }} - {{ item.medication_hrs }} hrs\\{% endfor %}\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {% for item in content.json_medications %}{{ item.medication_type }} - {{ item.medication_name }} - {{ item.medication_hrs }} hrs\\{% endfor %}\end{tabular}}}}%
 
@@
     %Diabetes
-    \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_daibetes_melitus}}\end{tabular}}}}%
-    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_daibetes_melitus}}\end{tabular}}}}%
-    %Hipertension
-    \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
-    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_arterial_hypertension}}\end{tabular}}}}%
-    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_arterial_hypertension}}\end{tabular}}}}%
-    %Cardiopatias
-    \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
-    \put(0.63928128,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_heart_disease}} \end{tabular}}}}%
-    \put(0.59572153,0.48073243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_heart_disease}} \end{tabular}}}}%
-    %Neumopatias
-    \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
-    \put(0.63928128,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_pneumopathies}}\end{tabular}}}}%
-    \put(0.59572153,0.45747395){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_pneumopathies}}\end{tabular}}}}%
-    %Trauma
-    \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
-    \put(0.63928128,0.43527803){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_trauma}}\end{tabular}}}}%
-    \put(0.59572153,0.43421546){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_trauma}}\end{tabular}}}}%
-    %Alergy
-    \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
-    \put(0.63928128,0.41201958){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.detail_pat_history_alergy}}\end{tabular}}}}%
-    \put(0.59572153,0.410957){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.pathological_history_alergy}}\end{tabular}}}}%
-    %Other
-    \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
-    \put(0.63928128,0.38876109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.other_pathological_history}}\end{tabular}}}}%
+    %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
+    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_daibetes_melitus}}\end{tabular}}}}%
+    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_daibetes_melitus}}\end{tabular}}}}%
+
+    % %Hipertension
+    % \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
+    \put(0.11758108,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_arterial_hypertension}}\end{tabular}}}}%
+    \put(0.14099679,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_arterial_hypertension}}\end{tabular}}}}%
+
+    % %Cardiopatias
+    % \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
+    \put(0.11758108,0.15476708){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_heart_disease}} \end{tabular}}}}%
+    \put(0.14099679,0.15474248){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_heart_disease}} \end{tabular}}}}%
+
+    % %Neumopatias
+    % \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
+    \put(0.11672491,0.14561334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_pneumopathies}}\end{tabular}}}}%
+    \put(0.14014062,0.14558873){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_pneumopathies}}\end{tabular}}}}%
+
+    % %Trauma
+    % \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
+    \put(0.11758108,0.13647739){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_trauma}}\end{tabular}}}}%
+    \put(0.14099679,0.13639128){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_trauma}}\end{tabular}}}}%
+
+    % %Alergy
+    % \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
+    \put(0.11758108,0.12728379){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.pathological_history_alergy}}\end{tabular}}}}%
+    \put(0.14099679,0.12719768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.detail_pat_history_alergy}}\end{tabular}}}}%
+
+    % %Other
+    % \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
+    \put(0.11758108,0.11881088){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.other_pathological_history}}\end{tabular}}}}%
     %\put(0.59572153,0.38769855){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
@@
     %Cabeza
-    \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_head}}\end{tabular}}}}%
-    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_head}}\end{tabular}}}}%
-    %Cara
-    \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_face}}\end{tabular}}}}%
-    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_face}}\end{tabular}}}}%
-    %Cuello
-    \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
-    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_neck}}\end{tabular}}}}%
-    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_neck}}\end{tabular}}}}%
-    %Torax
-    \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
-    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_torax}}\end{tabular}}}}%
-    \put(0.57421341,0.26602505){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_torax}}\end{tabular}}}}%
-    %Abdomen
-    \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
-    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_abdomen}}\end{tabular}}}}%
-    \put(0.57421363,0.24991392){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_abdomen}}\end{tabular}}}}%
-    %Extremidades
-    \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
-    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_limbs}}\end{tabular}}}}%
-    \put(0.59031192,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_limbs}}\end{tabular}}}}%
-    %Genitales
-    \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
-    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_genitals}}\end{tabular}}}}%
-    \put(0.58368309,0.21763312){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_genitals}}\end{tabular}}}}%
-    %Columna
-    \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
-    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.normal_spine}}\end{tabular}}}}%
-    \put(0.58218801,0.19630385){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.det_normal_spine}}\end{tabular}}}}%
+    % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_head}}\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_head}}\end{tabular}}}}%
+    % %Cara
+    % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_face}}\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_face}}\end{tabular}}}}%
+    % %Cuello
+    % \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
+    \put(0.5916532,0.60938371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_neck}}\end{tabular}}}}%
+    \put(0.61206298,0.60956465){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_neck}}\end{tabular}}}}%
+    % %Torax
+    % \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
+    \put(0.5916532,0.6002403){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_torax}}\end{tabular}}}}%
+    \put(0.61206298,0.60042124){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_torax}}\end{tabular}}}}%
+    % %Abdomen
+    % \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
+    \put(0.5916532,0.59110817){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_abdomen}}\end{tabular}}}}%
+    \put(0.61206298,0.59128911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_abdomen}}\end{tabular}}}}%
+    % %Extremidades
+    % \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
+    \put(0.5916532,0.58189295){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_limbs}}\end{tabular}}}}%
+    \put(0.61206298,0.58207389){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_limbs}}\end{tabular}}}}%
+    % %Genitales
+    % \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
+    \put(0.5916532,0.57279804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_genitals}}\end{tabular}}}}%
+    \put(0.61206298,0.57297897){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_genitals}}\end{tabular}}}}%
+    % %Columna
+    % \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
+    \put(0.5916532,0.56347221){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.normal_spine}}\end{tabular}}}}%
+    \put(0.61206298,0.56365314){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.det_normal_spine}}\end{tabular}}}}%
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_rhythm}}\end{tabular}}}}%
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_frequency}}\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_p}}\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_pr}}\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_axis_qrs}}\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qrs}}\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_st}}\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_t}}\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qt}}\end{tabular}}}}%
-    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_abnormalities}}\end{tabular}}}}%
-    %\put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.electro_interpretation}} {{content.json_physical_exploration}}\end{tabular}}}}%
+    \put(0.63149266,0.53664933){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_rhythm}}\end{tabular}}}}%
+    \put(0.73355182,0.53601477){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_frequency}}\end{tabular}}}}%
+    \put(0.83566643,0.53611718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_p}}\end{tabular}}}}%
+    \put(0.91520486,0.53649172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_pr}}\end{tabular}}}}%
+    \put(0.54866673,0.52688976){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_axis_qrs}}\end{tabular}}}}%
+    \put(0.64141646,0.52688976){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qrs}}\end{tabular}}}}%
+    \put(0.73569805,0.52651523){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_st}}\end{tabular}}}}%
+    \put(0.84094359,0.52614065){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_wave_t}}\end{tabular}}}}%
+    \put(0.91520486,0.52665127){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_qt}}\end{tabular}}}}%
+    \put(0.56987944,0.51728776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_abnormalities}}\end{tabular}}}}%
+    \put(0.65016698,0.50867338){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_interpretation}}\end{tabular}}}}%
     %Signos Vitales 1
-    {% for item in content.json_physical_exploration%}
-    \put(0.47899072,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.time }}\end{tabular}}}}%
-    \put(0.56346295,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.heart_rate }}\end{tabular}}}}%
-    \put(0.62325414,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.respiratory_rate}}\end{tabular}}}}%
-    \put(0.68836013,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.blood_pressure}}\end{tabular}}}}%
-    \put(0.74651878,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.temperature}}\end{tabular}}}}%
-    \put(0.81241818,0.62140804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.oxygen_saturation}}\end{tabular}}}}%
-    \put(0.87214411,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.glucometry}}\end{tabular}}}}%
-    \put(0.93275252,0.62149126){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{ item.glassgow_total }}\end{tabular}}}}%
+    {% for item in content.json_physical_exploration %}
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.time|slice:"11:" }} \end{tabular}}}}%
+    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.heart_rate }}\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.respiratory_rate}}\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.blood_pressure}}\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.temperature}}\end{tabular}}}}%
+    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.oxygen_saturation}}\end{tabular}}}}%
+    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glucometry}}\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glassgow_total }}\end{tabular}}}}%
     {% endfor %}
@@
     %\put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
-  \end{picture}
-\endgroup%
-\end{figure}
 
-\newpage
+    %Derivacion
+    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.derivation_type}} - {{content.derivation_hospital}}\end{tabular}}}}%
+    %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
+    \put(0.59086359,0.32494157){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.state_of_health}}\end{tabular}}}}%
+    \put(0.5890775,0.31621801){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.derivation_recive}}\end{tabular}}}}%
+    \put(0.83680772,0.30734249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.derivation_amount}}\end{tabular}}}}%
 
-\begin{figure}
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\input{paperless_template_6.pdf_tex}
+    %Finalizacion
+    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.demarcation_responsable}}\end{tabular}}}}%\
+    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.demarcation_relation}}\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.crew_medic}}\end{tabular}}}}%
+    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.crew_medic_id_card}}\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.crew_tum}}\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.crew_operator}}\end{tabular}}}}%
 
-\begingroup%
-  \makeatletter%
-  \providecommand\color[2][]{%
-    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-    \renewcommand\color[2][]{}%
-  }%
-  \providecommand\transparent[1]{%
-    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-    \renewcommand\transparent[1]{}%
-  }%
-  \providecommand\rotatebox[2]{#2}%
-  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-  \ifx\svgwidth\undefined%
-    \setlength{\unitlength}{782.27360219bp}%
-    \ifx\svgscale\undefined%
-      \relax%
-    \else%
-      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-    \fi%
-  \else%
-    \setlength{\unitlength}{\svgwidth}%
-  \fi%
-  \global\let\svgwidth\undefined%
-  \global\let\svgscale\undefined%
-  \makeatother%
-  \begin{picture}(1,0.77245213)%
-    \lineheight{1}%
-    \setlength\tabcolsep{0pt}%
-    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
-    %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
-    %Tratamiento
-    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.fix_treatment}} \end{tabular}}}}%
-    %Derivacion
-    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_type}}\end{tabular}}}}%
-    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
-    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.state_of_health}}\end{tabular}}}}%
-    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_recive}}\end{tabular}}}}%
-    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_amount}}\end{tabular}}}}%
-    %Finalizacion
-    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
-    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_relation}}\end{tabular}}}}%
-    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic}}\end{tabular}}}}%
-    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic_id_card}}\end{tabular}}}}%
-    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_tum}}\end{tabular}}}}%
-    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_operator}}\end{tabular}}}}%
-    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ {{ content.demarcation_responsable }} }}\end{tabular}}}}%
-    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
-    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
+    {% if content.have_medic_signature %}
+      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
+      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+    {% endif %}
+
+    {% if content.have_client_signature %}
+    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
+    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.demarcation_responsable}}\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+    {% endif %}
 
@@
 
+% \newpage
+
+% \begin{figure}
+%   \centering
+%   \def\svgwidth{\columnwidth}
+%   %\input{paperless_template_6.pdf_tex}
+
+% \begingroup%
+%   \makeatletter%
+%   \providecommand\color[2][]{%
+%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
+%     \renewcommand\color[2][]{}%
+%   }%
+%   \providecommand\transparent[1]{%
+%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
+%     \renewcommand\transparent[1]{}%
+%   }%
+%   \providecommand\rotatebox[2]{#2}%
+%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
+%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
+%   \ifx\svgwidth\undefined%
+%     \setlength{\unitlength}{782.27360219bp}%
+%     \ifx\svgscale\undefined%
+%       \relax%
+%     \else%
+%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
+%     \fi%
+%   \else%
+%     \setlength{\unitlength}{\svgwidth}%
+%   \fi%
+%   \global\let\svgwidth\undefined%
+%   \global\let\svgscale\undefined%
+%   \makeatother%
+%   \begin{picture}(1,0.77245213)%
+%     \lineheight{1}%
+%     \setlength\tabcolsep{0pt}%
+%     \put(0,0){\includegraphics[width=\unitlength,page=1]{parte_medico_master}}%
+%     {% if content.have_client_signature %}
+%     \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
+%     \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
+%     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
+%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
+%     {% endif %}
+%     {% if content.have_medic_signature %}
+%     \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
+%     \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+%     {% endif %}
+%     %Impresion diagnostica
+%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
+%     %Tratamiento
+%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%
+%     %Derivacion
+%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_type}}\end{tabular}}}}%
+%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
+%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.state_of_health}}\end{tabular}}}}%
+%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_recive}}\end{tabular}}}}%
+%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_amount}}\end{tabular}}}}%
+%     %Finalizacion
+%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%\
+
+%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_relation}}\end{tabular}}}}%
+%     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic}}\end{tabular}}}}%
+%     \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic_id_card}}\end{tabular}}}}%
+%     \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_tum}}\end{tabular}}}}%
+%     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_operator}}\end{tabular}}}}%
+%     %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ {{ content.demarcation_responsable }} }}\end{tabular}}}}%
+%     %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+%     %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+%     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
+
+%   \end{picture}
+% \endgroup%
+% \end{figure}
+
 \end{document}

### 2022-08-24 ersteops/templates/printpdf/rendered_template.tex
update template

--- 2022-08-19 ersteops/templates/printpdf/rendered_template.tex
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 51
+    %    \textbf{Consulta \#:} 58
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf51
+    %    \textbf58
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 51
+%     %    \textbf{Consulta \#:} 58
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 51 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 51 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 58 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 58 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
 %     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-006 }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
 
@@
     \setlength\tabcolsep{0pt}%
-    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_1}}%
+    \put(0,0){\includegraphics[width=\unitlength,page=1]{master_parte_medico}}%
     %\put(0.31336785,0.38838718){\includegraphics[scale=1]{test_image}}%
     %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
+    %Times
+    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 2022-07-22\end{tabular}}}}%
+    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
+    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
 
     %Folio
-    \put(0.91336785,0.68838718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 51\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 58\end{tabular}}}}%
 
-    \put(0.42638971,0.73960084){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 11\end{tabular}}}}%
-    \put(0.43014479,0.72364315){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont M011\end{tabular}}}}%
-   	\put(0.33829987,0.69381105){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.39132267,0.67728521){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont QPR-006\end{tabular}}}}%
+    \put(0.10902655,0.55515604){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 11\end{tabular}}}}%
+    \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
 
     %Paciente
-    \put(0.09655761,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont F55\end{tabular}}}}%
-    \put(0.20912356,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 5556782349\end{tabular}}}}%
-    \put(0.3268484,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Masculino\end{tabular}}}}%
-    \put(0.42764439,0.62853648){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 14\end{tabular}}}}%
-    \put(0.12766308,0.61324599){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Lillia Sanchez Jaime\end{tabular}}}}%
-    \put(0.02575936,0.58169366){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Moni Sanchez Jaime\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.01999075,0.53033139){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.01999075,0.48794778){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont  NA\end{tabular}}}}%
-    \put(0.09106678,0.46594263){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.12588643,0.44615019){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.23723674,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.07146203,0.50540156){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  NA\end{tabular}}}}%
+    \put(0.07920229,0.49404644){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.37437746,0.49499384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.0159714,0.1825995){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
     %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
     %Generales
-    \put(0.12027596,0.41209986){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
-    \put(0.30209431,0.41082061){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
-    \put(0.30209431,0.39566916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
+    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+
+      \put(0.3007691,0.47620579){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
+
     %Trauma
-    \put(0.21257984,0.38532216){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
     %Ojo Izquierdo
-    \put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: \end{tabular}}}}%
+    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: Isocoria,Midriasis,\end{tabular}}}}%
     %Ojo Derecho
-    \put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  \end{tabular}}}}%
-    \put(0.016641,0.38301062){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 
+    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  Miosis,Anisocoria,\end{tabular}}}}%
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}
     \end{tabular}}}}%
@@
     %Via Aerea
-    \put(0.01535741,0.34684125){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.32505266,0.47551987){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+
+        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+    %inmovilizacion
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}
+    \end{tabular}}}}%
+
+    %Impresion diagnostica
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    %Tratamiento
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
 
@@
     %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
-    \put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
 
@@
     %Diabetes
-    \put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.63928128,0.52831197){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59572153,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
-    %Hipertension
-    \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
-    \put(0.63928128,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59572153,0.50399092){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
-    %Cardiopatias
-    \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
-    \put(0.63928128,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
-    \put(0.59572153,0.48073243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No \end{tabular}}}}%        
-    %Neumopatias
-    \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
-    \put(0.63928128,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59572153,0.45747395){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
-    %Trauma
-    \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
-    \put(0.63928128,0.43527803){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59572153,0.43421546){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
-    %Alergy
-    \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
-    \put(0.63928128,0.41201958){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59572153,0.410957){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
-    %Other
-    \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
-    \put(0.63928128,0.38876109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
+    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
+    % %Hipertension
+    % \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
+    \put(0.11758108,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.14099679,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
+    % %Cardiopatias
+    % \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
+    \put(0.11758108,0.15476708){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No \end{tabular}}}}%
+    \put(0.14099679,0.15474248){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+
+    % %Neumopatias
+    % \put(0.48529688,0.45853652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Neumopatias\end{tabular}}}}%
+    \put(0.11672491,0.14561334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.14014062,0.14558873){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
+    % %Trauma
+    % \put(0.48715137,0.43527249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Quirurgicos/trauma:\end{tabular}}}}%
+    \put(0.11758108,0.13647739){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.14099679,0.13639128){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
+    % %Alergy
+    % \put(0.48715137,0.41208615){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Alergias\end{tabular}}}}%
+    \put(0.11758108,0.12728379){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.14099679,0.12719768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
+    % %Other
+    % \put(0.48715137,0.38762916){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Otros\end{tabular}}}}%
+    \put(0.11758108,0.11881088){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
     %\put(0.59572153,0.38769855){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont No\end{tabular}}}}%
@@
     %Cabeza
-    \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.53919296,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57282362,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    %Cara
-    \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.53910339,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57184628,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    %Cuello
-    \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
-    \put(0.53910318,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57366532,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Torax
-    \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
-    \put(0.53965121,0.26504573){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57421341,0.26602505){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Abdomen
-    \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
-    \put(0.53965149,0.24893455){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.57421363,0.24991392){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Extremidades
-    \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
-    \put(0.5709012,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.59031192,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Genitales
-    \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
-    \put(0.55290888,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.58368309,0.21763312){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Columna
-    \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
-    \put(0.55094037,0.19532448){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
-    \put(0.58218801,0.19630385){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Cara
+    % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Cuello
+    % \put(0.48349046,0.28131895){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cuello\end{tabular}}}}%
+    \put(0.5916532,0.60938371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.60956465){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Torax
+    % \put(0.48339183,0.26495693){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Tórax\end{tabular}}}}%
+    \put(0.5916532,0.6002403){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.60042124){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Abdomen
+    % \put(0.48416864,0.24905109){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Abdomen\end{tabular}}}}%
+    \put(0.5916532,0.59110817){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.59128911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Extremidades
+    % \put(0.48373092,0.23278776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Extremidades\end{tabular}}}}%
+    \put(0.5916532,0.58189295){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.58207389){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Genitales
+    % \put(0.48348429,0.2166538){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Genitales\end{tabular}}}}%
+    \put(0.5916532,0.57279804){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.57297897){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    % %Columna
+    % \put(0.48349046,0.2025433){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Columna \\Vertebral\end{tabular}}}}%
+    \put(0.5916532,0.56347221){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.61206298,0.56365314){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
     %Electro
-    \put(0.53673588,0.1536906){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.63974772,0.15416371){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.73901494,0.1542802){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.80638047,0.15431264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.54883898,0.14280022){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61275927,0.14232657){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.66200174,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.7368123,0.14137953){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.809729,0.1423264){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%    
-    \put(0.49140242,0.11457272){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %\put(0.49140242,0.04639155){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA []\end{tabular}}}}%
+    \put(0.63149266,0.53664933){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.73355182,0.53601477){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.83566643,0.53611718){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.91520486,0.53649172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.54866673,0.52688976){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.64141646,0.52688976){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.73569805,0.52651523){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.84094359,0.52614065){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.91520486,0.52665127){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.56987944,0.51728776){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.65016698,0.50867338){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
     %Signos Vitales 1
@@
     %\put(0.93275252,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 826\end{tabular}}}}%
-  \end{picture}
-\endgroup%
-\end{figure}
 
-\newpage
+    %Derivacion
+    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA - NA\end{tabular}}}}%
+    %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.59086359,0.32494157){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5890775,0.31621801){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.83680772,0.30734249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
 
-\begin{figure}
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\input{paperless_template_6.pdf_tex}
+    %Finalizacion
+    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
+    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
+    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
 
-\begingroup%
-  \makeatletter%
-  \providecommand\color[2][]{%
-    \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-    \renewcommand\color[2][]{}%
-  }%
-  \providecommand\transparent[1]{%
-    \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-    \renewcommand\transparent[1]{}%
-  }%
-  \providecommand\rotatebox[2]{#2}%
-  \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-  \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-  \ifx\svgwidth\undefined%
-    \setlength{\unitlength}{782.27360219bp}%
-    \ifx\svgscale\undefined%
-      \relax%
-    \else%
-      \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-    \fi%
-  \else%
-    \setlength{\unitlength}{\svgwidth}%
-  \fi%
-  \global\let\svgwidth\undefined%
-  \global\let\svgscale\undefined%
-  \makeatother%
-  \begin{picture}(1,0.77245213)%
-    \lineheight{1}%
-    \setlength\tabcolsep{0pt}%
-    \put(0,0){\includegraphics[width=\unitlength,page=1]{paperless_template_page_2}}%
+      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
+      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
 
-    \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-
-    \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
-    \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
-
-    %Impresion diagnostica
-    \put(0.02433222,0.72271027){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Tratamiento
-    \put(0.02377709,0.34714045){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA \end{tabular}}}}%
-    %Derivacion
-    \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
-    \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-    \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    %Finalizacion
-    \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\
-
-    \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
-    \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
-    \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
-    \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
-    %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-    \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
-    %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-    %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
-    %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
 
@@
 
+% \newpage
+
+% \begin{figure}
+%   \centering
+%   \def\svgwidth{\columnwidth}
+%   %\input{paperless_template_6.pdf_tex}
+
+% \begingroup%
+%   \makeatletter%
+%   \providecommand\color[2][]{%
+%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
+%     \renewcommand\color[2][]{}%
+%   }%
+%   \providecommand\transparent[1]{%
+%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
+%     \renewcommand\transparent[1]{}%
+%   }%
+%   \providecommand\rotatebox[2]{#2}%
+%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
+%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
+%   \ifx\svgwidth\undefined%
+%     \setlength{\unitlength}{782.27360219bp}%
+%     \ifx\svgscale\undefined%
+%       \relax%
+%     \else%
+%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
+%     \fi%
+%   \else%
+%     \setlength{\unitlength}{\svgwidth}%
+%   \fi%
+%   \global\let\svgwidth\undefined%
+%   \global\let\svgscale\undefined%
+%   \makeatother%
+%   \begin{picture}(1,0.77245213)%
+%     \lineheight{1}%
+%     \setlength\tabcolsep{0pt}%
+%     \put(0,0){\includegraphics[width=\unitlength,page=1]{parte_medico_master}}%
+%     
+%     \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
+%     \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
+%     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
+%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     
+%     
+%     \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
+%     \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+%     
+%     %Impresion diagnostica
+%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+%     %Tratamiento
+%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+%     %Derivacion
+%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
+%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     %Finalizacion
+%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\
+
+%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
+%     \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
+%     \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
+%     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
+%     %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
+%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
+%     %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
+%     %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
+%     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
+
+%   \end{picture}
+% \endgroup%
+% \end{figure}
+
 \end{document}

### 2022-08-26 ersteops/templates/printpdf/paperless_template.tex
fix treatmen text

@@
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} }\end{tabular}}}}%
 

### 2022-08-26 ersteops/templates/printpdf/rendered_template.tex
fix treatmen text

@@
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{\fontfamily{lmss}\selectfont\scriptsize NA }\end{tabular}}}}%
 

### 2022-08-26 ersteops/templates/printpdf/rendered_template.tex
fix missing lines

--- 2022-08-24 ersteops/templates/printpdf/rendered_template.tex
@@
     %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 58
+    %    \textbf{Consulta \#:} 57
     % }
@@
     % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf58
+    %    \textbf57
     % }
@@
 %     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 58
+%     %    \textbf{Consulta \#:} 57
 %     % }
 %     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 58 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 58 }\end{tabular}}}}%
+%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 57 }\end{tabular}}}}%
+% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 57 }\end{tabular}}}}%
 %    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
 %     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
+%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-001 }\end{tabular}}}}%
 
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 58\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 57\end{tabular}}}}%
 
@@
    	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
 
     %Paciente
-    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - NA\end{tabular}}}}%
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
-    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5\end{tabular}}}}%
-    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Moni Sanchez Jaime\end{tabular}}}}%
-    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Femenino\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 13\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asdasd asd\end{tabular}}}}%
 
     %Paciente desconocido
-    \put(0.23723674,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.07146203,0.50540156){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  NA\end{tabular}}}}%
-    \put(0.07920229,0.49404644){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.37437746,0.49499384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.23723674,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdasdas dasd asd\end{tabular}}}}%
+    \put(0.07146203,0.50540156){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  as dasd asd asda\end{tabular}}}}%
+    \put(0.07920229,0.49404644){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize as dasd asd as\end{tabular}}}}%
+    \put(0.37437746,0.49499384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize a sdas dasds asd\end{tabular}}}}%
 
     %Padecimiento
-    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdasdsad asd as\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asdasdsad asd as\end{tabular}}}}%
 
     %Generales
-    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
-    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Hogar \end{tabular}}}}%
+    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Traslado \end{tabular}}}}%
 
-      \put(0.3007691,0.47620579){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
+      \put(0.30180123,0.46556814){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
 
     %Trauma
-    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Craneal\\\fontfamily{lmss}\selectfont\scriptsize Craneoencefalico\\\end{tabular}}}}%
     %Ojo Izquierdo
-    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: Isocoria,Midriasis,\end{tabular}}}}%
+    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: Isocoria,\end{tabular}}}}%
     %Ojo Derecho
-    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  Miosis,Anisocoria,\end{tabular}}}}%
-    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}
+    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  Midriasis,\end{tabular}}}}%
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cefalea\\\fontfamily{lmss}\selectfont\scriptsize Sincope\\
     \end{tabular}}}}%
@@
 
-        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+        \put(0.45601685,0.41487724){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
 
     %inmovilizacion
-    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Columna Cervical\\\fontfamily{lmss}\selectfont\scriptsize Columna Toracica\\
     \end{tabular}}}}%
@@
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdasd asd\end{tabular}}}}%
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd \end{tabular}}}}%
 
@@
     %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
-    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asddfasdasd\end{tabular}}}}%
 
@@
     % \put(0.48529688,0.48172564){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cardiopatias \end{tabular}}}}%
-    \put(0.11758108,0.15476708){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No \end{tabular}}}}%
-    \put(0.14099679,0.15474248){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.11758108,0.15476708){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si \end{tabular}}}}%
+    \put(0.14099679,0.15474248){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd \end{tabular}}}}%
 
@@
     % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdasdasd\end{tabular}}}}%
     % %Cara
     % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asds a\end{tabular}}}}%
     % %Cuello
@@
     %Derivacion
-    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA - NA\end{tabular}}}}%
-    %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-    \put(0.59086359,0.32494157){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.5890775,0.31621801){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.83680772,0.30734249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si - dalinde\end{tabular}}}}%
+    %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont dalinde\end{tabular}}}}%
+    \put(0.59086359,0.32494157){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Estable\end{tabular}}}}%
+    \put(0.5890775,0.31621801){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize este es el medico\end{tabular}}}}%
+    \put(0.83680772,0.30734249){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 120\end{tabular}}}}%
 
     %Finalizacion
-    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
-    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asdas\end{tabular}}}}%\
+    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize as dasd\end{tabular}}}}%
     \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
@@
     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asdas\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asd asd asdas\end{tabular}}}}%
 
@@
 %     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asd asd asdas\end{tabular}}}}%
+%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asd asd asdas\end{tabular}}}}%
 %     
@@
 %     %Impresion diagnostica
-%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdasd asd\end{tabular}}}}%
 %     %Tratamiento
-%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd \end{tabular}}}}%
 %     %Derivacion
-%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Si\end{tabular}}}}%
+%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont dalinde\end{tabular}}}}%
+%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Estable\end{tabular}}}}%
+%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont este es el medico\end{tabular}}}}%
+%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 120\end{tabular}}}}%
 %     %Finalizacion
-%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\
+%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asd asd asdas\end{tabular}}}}%\
 
-%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont as dasd\end{tabular}}}}%
 %     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
@@
 %     %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
+%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ asd asd asdas }}\end{tabular}}}}%
 %     %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%

### 2022-08-26 ersteops/printpdf/views.py

@@ -344,7 +344,7 @@ def add_line_breaks(break_string,every):
   #res = '\n '.join(a + b for a, b in zip(break_string[::3], break_string[1::3]))
   #return res
   # initializing K
-  K = '\n'
+  K = '\n \fontfamily{lmss}\selectfont\scriptsize'
  
   # initializing N
   N = every

### 2022-08-29 ersteops/templates/printpdf/paperless_template.tex
fix missing lines
update format

--- 2022-08-24 ersteops/templates/printpdf/paperless_template.tex
@@
 \begin{document}
-\fontfamily{lmss}\selectfont
-    % Include Background in ./prescript/media/media/template_v1.pdf
-    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
-    % Define page content
-    %\textsf{\large{
-    %\begin{changemargin}{1.5cm}{1.2cm}
-        %\begin{enumerate}
-            %{{ all_medications }}
-            %bla!
-        %\end{enumerate}
-    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} {{ content.id }}
-    % }
-    % }}}
-        % Indicaciones Extra
-        % \begin{enumerate}
-        %     \textbf{Indicaciones Extra: \\ } {{ all_medications }}
-        % \end{enumerate}
-    %\end{changemargin}
-    %}}
-    % \begin{picture}(1,0.77272727)%
-    %     %Consulta    
-    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{{ content.id }}
-    % }
-    % }}}
-    % \end{picture}
-% \begingroup%
-%   \makeatletter%
-%   \providecommand\color[2][]{%
-%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-%     \renewcommand\color[2][]{}%
-%   }%
-%   \providecommand\transparent[1]{%
-%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-%     \renewcommand\transparent[1]{}%
-%   }%
-%   \providecommand\rotatebox[2]{#2}%
-%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
-%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-%   \ifx\svgwidth\undefined%
-%     \setlength{\unitlength}{792bp}%
-%     \ifx\svgscale\undefined%
-%       \relax%
-%     \else%
-%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-%     \fi%
-%   \else%
-%     \setlength{\unitlength}{\svgwidth}%
-%   \fi%
-%   \global\let\svgwidth\undefined%
-%   \global\let\svgscale\undefined%
-%   \makeatother%
-%   \begin{picture}(1,0.77272727)%
-%     \lineheight{1}%
-%     \setlength\tabcolsep{0pt}%
-%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%
-
-%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} {{ content.id }}
-%     % }
-%     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido {{content.id}} }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.id}} }\end{tabular}}}}%
-%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit }} }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit_type}} }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ {{content.service_unit_plate}} }\end{tabular}}}}%
-
-%   \end{picture}%
-% \endgroup%
-
-\begin{figure}
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\input{paperless_template_6.pdf_tex}
+\fontfamily{lmss}\selectfont\scriptsize
 
@@
   \makeatother%
+
   \begin{picture}(1,0.77245213)%
@@
     \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_traumatics %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor %}\end{tabular}}}}%
-    %Ojo Izquierdo
-    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: {% for item in content.json_pupil_state_left%}{{ item }},{% endfor %}\end{tabular}}}}%
-    %Ojo Derecho
-    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  {% for item in content.json_pupil_state_right%}{{ item }},{% endfor%}\end{tabular}}}}%
-    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_consultation_reason %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
-    \end{tabular}}}}%
+    %Motivo de Consulta
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}{% for item in content.json_consultation_reason %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}\end{tabular}}}}%
     %to_fix
@@
     %inmovilizacion
-    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}{% for item in content.json_inmovilization_type %}\fontfamily{lmss}\selectfont\scriptsize {{ item }}\\{% endfor%}
-    \end{tabular}}}}%
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {% for item in content.json_inmovilization_type %}{{ item }}\\{% endfor %} \end{tabular}}}}%
 
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
     %Tratamiento
@@
     \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glucometry}}\end{tabular}}}}%
-    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glassgow_total }}\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glassgow_total }}\end{tabular}} }}%
     {% endfor %}
@@
     %Derivacion
-    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.derivation_type}} - {{content.derivation_hospital}}\end{tabular}}}}%
+    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.derivation_type}} - {{content.derivation_hospital}}\end{tabular}} }}%
     %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
@@
   \end{picture}
+
 \endgroup%
-\end{figure}
-
-% \newpage
-
-% \begin{figure}
-%   \centering
-%   \def\svgwidth{\columnwidth}
-%   %\input{paperless_template_6.pdf_tex}
-
-% \begingroup%
-%   \makeatletter%
-%   \providecommand\color[2][]{%
-%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-%     \renewcommand\color[2][]{}%
-%   }%
-%   \providecommand\transparent[1]{%
-%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-%     \renewcommand\transparent[1]{}%
-%   }%
-%   \providecommand\rotatebox[2]{#2}%
-%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-%   \ifx\svgwidth\undefined%
-%     \setlength{\unitlength}{782.27360219bp}%
-%     \ifx\svgscale\undefined%
-%       \relax%
-%     \else%
-%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-%     \fi%
-%   \else%
-%     \setlength{\unitlength}{\svgwidth}%
-%   \fi%
-%   \global\let\svgwidth\undefined%
-%   \global\let\svgscale\undefined%
-%   \makeatother%
-%   \begin{picture}(1,0.77245213)%
-%     \lineheight{1}%
-%     \setlength\tabcolsep{0pt}%
-%     \put(0,0){\includegraphics[width=\unitlength,page=1]{parte_medico_master}}%
-%     {% if content.have_client_signature %}
-%     \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
-%     \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
-%     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
-%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%
-%     {% endif %}
-%     {% if content.have_medic_signature %}
-%     \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
-%     \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
-%     {% endif %}
-%     %Impresion diagnostica
-%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
-%     %Tratamiento
-%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%
-%     %Derivacion
-%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_type}}\end{tabular}}}}%
-%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_hospital}}\end{tabular}}}}%
-%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.state_of_health}}\end{tabular}}}}%
-%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_recive}}\end{tabular}}}}%
-%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.derivation_amount}}\end{tabular}}}}%
-%     %Finalizacion
-%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_responsable}}\end{tabular}}}}%\
-
-%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.demarcation_relation}}\end{tabular}}}}%
-%     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic}}\end{tabular}}}}%
-%     \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_medic_id_card}}\end{tabular}}}}%
-%     \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_tum}}\end{tabular}}}}%
-%     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont {{content.crew_operator}}\end{tabular}}}}%
-%     %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ {{ content.demarcation_responsable }} }}\end{tabular}}}}%
-%     %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-%     %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
-%     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
-
-%   \end{picture}
-% \endgroup%
-% \end{figure}
 

### 2022-08-29 ersteops/templates/printpdf/rendered_template.tex
update format

--- 2022-08-24 ersteops/templates/printpdf/rendered_template.tex
@@
 \begin{document}
-\fontfamily{lmss}\selectfont
-    % Include Background in ./prescript/media/media/template_v1.pdf
-    % \AddToShipoutPictureBG{\ifthenelse{\isodd{\value{page}}}{\includegraphics{laam_template}}{\includegraphics{laam_template}}}
-    % Define page content
-    %\textsf{\large{
-    %\begin{changemargin}{1.5cm}{1.2cm}
-        %\begin{enumerate}
-            %
-            %bla!
-        %\end{enumerate}
-    %         \put(1,1){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf{Consulta \#:} 58
-    % }
-    % }}}
-        % Indicaciones Extra
-        % \begin{enumerate}
-        %     \textbf{Indicaciones Extra: \\ } 
-        % \end{enumerate}
-    %\end{changemargin}
-    %}}
-    % \begin{picture}(1,0.77272727)%
-    %     %Consulta    
-    % \put(200,0){\parbox[t]{3cm}{\textsf{\large{
-    %    \textbf58
-    % }
-    % }}}
-    % \end{picture}
-% \begingroup%
-%   \makeatletter%
-%   \providecommand\color[2][]{%
-%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-%     \renewcommand\color[2][]{}%
-%   }%
-%   \providecommand\transparent[1]{%
-%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-%     \renewcommand\transparent[1]{}%
-%   }%
-%   \providecommand\rotatebox[2]{#2}%
-%   \newcommand\scaleInNode[1][1]{\tikzset{execute at begin node={\normalsize\larger[#1]}}}
-%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-%   \ifx\svgwidth\undefined%
-%     \setlength{\unitlength}{792bp}%
-%     \ifx\svgscale\undefined%
-%       \relax%
-%     \else%
-%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-%     \fi%
-%   \else%
-%     \setlength{\unitlength}{\svgwidth}%
-%   \fi%
-%   \global\let\svgwidth\undefined%
-%   \global\let\svgscale\undefined%
-%   \makeatother%
-%   \begin{picture}(1,0.77272727)%
-%     \lineheight{1}%
-%     \setlength\tabcolsep{0pt}%
-%     \put(0,0){\includegraphics[width=\unitlength,page=1]{laam_template}}%
-
-%     % \put(0.01140896,0.54355203){\parbox[t]{3cm}{\textsf{\large{
-%     %    \textbf{Consulta \#:} 58
-%     % }
-%     % }}}
-%     % \put(0.01140896,0.54355203){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{Paciente desconocido 58 }\end{tabular}}}}%
-% 	\put(0.42718184,0.73912713){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ 58 }\end{tabular}}}}%
-%    	\put(0.42718184,0.72336542){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ M011 }\end{tabular}}}}%
-%     \put(0.3690564,0.69389968){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ ASISTENCIA BASICA }\end{tabular}}}}%
-%     \put(0.39254546,0.6775768){\color[rgb]{0,0,0}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textit{ QPR-005 }\end{tabular}}}}%
-
-%   \end{picture}%
-% \endgroup%
-
-\begin{figure}
-  \centering
-  \def\svgwidth{\columnwidth}
-  %\input{paperless_template_6.pdf_tex}
+\fontfamily{lmss}\selectfont\scriptsize
 
@@
     \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
-    %Ojo Izquierdo
-    %\put(0.20991809,0.36213786){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Izquierdo: Isocoria,Midriasis,\end{tabular}}}}%
-    %Ojo Derecho
-    %\put(0.20991809,0.35077424){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Ojo Derecho:  Miosis,Anisocoria,\end{tabular}}}}%
-    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}
-    \end{tabular}}}}%
+    %Motivo de Consulta
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
     %to_fix
@@
     %inmovilizacion
-    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}
-    \end{tabular}}}}%
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  \end{tabular}}}}%
 
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ NA\end{tabular}}}}%
     %Tratamiento
@@
     %Derivacion
-    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA - NA\end{tabular}}}}%
+    \put(0.56632851,0.33413518){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA - NA\end{tabular}} }}%
     %\put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
@@
   \end{picture}
+
 \endgroup%
-\end{figure}
-
-% \newpage
-
-% \begin{figure}
-%   \centering
-%   \def\svgwidth{\columnwidth}
-%   %\input{paperless_template_6.pdf_tex}
-
-% \begingroup%
-%   \makeatletter%
-%   \providecommand\color[2][]{%
-%     \errmessage{(Inkscape) Color is used for the text in Inkscape, but the package 'color.sty' is not loaded}%
-%     \renewcommand\color[2][]{}%
-%   }%
-%   \providecommand\transparent[1]{%
-%     \errmessage{(Inkscape) Transparency is used (non-zero) for the text in Inkscape, but the package 'transparent.sty' is not loaded}%
-%     \renewcommand\transparent[1]{}%
-%   }%
-%   \providecommand\rotatebox[2]{#2}%
-%   \newcommand*\fsize{\dimexpr\f@size pt\relax}%
-%   \newcommand*\lineheight[1]{\fontsize{\fsize}{#1\fsize}\selectfont}%
-%   \ifx\svgwidth\undefined%
-%     \setlength{\unitlength}{782.27360219bp}%
-%     \ifx\svgscale\undefined%
-%       \relax%
-%     \else%
-%       \setlength{\unitlength}{\unitlength * \real{\svgscale}}%
-%     \fi%
-%   \else%
-%     \setlength{\unitlength}{\svgwidth}%
-%   \fi%
-%   \global\let\svgwidth\undefined%
-%   \global\let\svgscale\undefined%
-%   \makeatother%
-%   \begin{picture}(1,0.77245213)%
-%     \lineheight{1}%
-%     \setlength\tabcolsep{0pt}%
-%     \put(0,0){\includegraphics[width=\unitlength,page=1]{parte_medico_master}}%
-%     
-%     \put(0.78960956,0.18450476){\includegraphics[scale=0.5]{client_signature}}%
-%     \put(0.64203741,0.01450476){\includegraphics[scale=0.5]{client_signature}}%
-%     %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-%     \put(0.64203741,0.20450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     
-%     
-%     \put(0.78960956,0.46450476){\includegraphics[scale=0.5,frame]{signature_medic}}%
-%     \put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
-%     
-%     %Impresion diagnostica
-%      \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-%     %Tratamiento
-%      \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
-%     %Derivacion
-%     \put(0.56751227,0.6911999){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.56751227,0.6721787){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.60035291,0.65502334){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.60169212,0.63688865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%    
-%     \put(0.54544497,0.61971664){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     %Finalizacion
-%     \put(0.57431346,0.56661945){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%\
-
-%     \put(0.6223905,0.54640692){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-%     \put(0.54203741,0.50578489){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Dr.Chapatin\end{tabular}}}}%
-%     \put(0.59900976,0.48543641){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont XXX-XXXX-XXX\end{tabular}}}}%
-%     \put(0.53065814,0.46522944){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cacharpo\end{tabular}}}}%
-%     \put(0.55816754,0.44488927){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont El Operador\end{tabular}}}}%
-%     %\put(0.92413649,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X4 }}\end{tabular}}}}%
-%     \put(0.65327278,0.35657174){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ NA }}\end{tabular}}}}%
-%     %\put(0.77324116,0.32194201){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X3 }}\end{tabular}}}}%
-%     %\put(0.76701121,0.33763243){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{ X2 }}\end{tabular}}}}%
-%     %\put(0.66004404,0.33814317){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{\textit{☑︎}}\end{tabular}}}}%
-
-%   \end{picture}
-% \endgroup%
-% \end{figure}
 

### 2022-08-29 ersteops/printpdf/views.py

@@ -298,8 +298,8 @@ def get_medical_report(pk):
   medical_Report['json_pupil_state_right'] = list(eval(raw_medical_Report.pupil_state_right))
   medical_Report['json_traumatics'] = list(eval(raw_medical_Report.traumatics))    
   medical_Report['json_inmovilization_type'] = list(eval(raw_medical_Report.inmovilization_type))
-  medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,67)
-  medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,41)
+  medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,50)
+  medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,38)
   medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,41)  
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
@@ -344,7 +344,7 @@ def add_line_breaks(break_string,every):
   #res = '\n '.join(a + b for a, b in zip(break_string[::3], break_string[1::3]))
   #return res
   # initializing K
-  K = '\n \fontfamily{lmss}\selectfont\scriptsize'
+  K = '\n'
  
   # initializing N
   N = every

### 2022-08-30 ersteops/templates/printpdf/rendered_template.tex
fix treatnment

@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 58\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 59\end{tabular}}}}%
 
@@
    	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
 
@@
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
-    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5\end{tabular}}}}%
-    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Moni Sanchez Jaime\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 0\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
     \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
@@
 
-        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
     %inmovilizacion
@@
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ NA\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ estas son las descripciones de lesione \\ sadas dasd asasd ans,.dasn asd asd a \\s asd asd asd asd asadsd asdas asd as \\ asd asd asd asdas das as asd,.mn,.m, \\asdm .dasd \\asd asd asdasd asd as\end{tabular}}}}%
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize este es el tratamiento que al fional falla,debemo \\ hacsr que no fale por que si falla ya valio ber \\a las calmadas y asi \\esta es otra linea del trat \\moento a ver cuantos caracteres son \\ \end{tabular}}}}%
 
@@
 
-      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
-      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
-
-    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
-    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
-
   \end{picture}

### 2022-08-30 ersteops/printpdf/views.py

@@ -298,7 +298,7 @@ def get_medical_report(pk):
   medical_Report['json_pupil_state_right'] = list(eval(raw_medical_Report.pupil_state_right))
   medical_Report['json_traumatics'] = list(eval(raw_medical_Report.traumatics))    
   medical_Report['json_inmovilization_type'] = list(eval(raw_medical_Report.inmovilization_type))
-  medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,50)
+  medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,49)
   medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,38)
   medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,41)  
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)

### 2022-08-30 ersteops/templates/printpdf/paperless_template.tex
add crum data, and fix vitals display

@@
     %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
+
+    %CRUM
+    {% if content.crum and content.crum  != 'NA' %}
+    \put(0.03139789,0.68674397){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{CRUM}\end{tabular}}}}%    
+    \put(0.03100834,0.67744828){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Folio: {{content.crum}}\end{tabular}}}}%
+    \put(0.03122157,0.66837832){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hospital: {{content.crum_hospital}}\end{tabular}}}}%
+    \put(0.03156192,0.65971048){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Médico: {{content.crum_reception}}\end{tabular}}}}%
+    \put(0.0314717,0.64991652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Notas: {{content.crum_notes}}\end{tabular}}}}%
+    {% endif %}
+
     %Times
@@
     \put(0.65016698,0.50867338){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.electro_interpretation}}\end{tabular}}}}%
+
     %Signos Vitales 1
     {% for item in content.json_physical_exploration %}
+    {% if forloop.counter0 == 0 %}
     \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.time|slice:"11:" }} \end{tabular}}}}%
@@
     \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glassgow_total }}\end{tabular}} }}%
+    {% endif %}
+
+    %Signos Vitales 2
+    {% if forloop.counter0 == 1 %}
+    \put(0.02662482,0.05996336){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.time|slice:"11:" }}\end{tabular}}}}%
+    \put(0.0575196,0.05986849){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.heart_rate }}\end{tabular}}}}%
+    \put(0.13048304,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.respiratory_rate }}\end{tabular}}}}%
+    \put(0.20938116,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.blood_pressure }}\end{tabular}}}}%
+    \put(0.26551354,0.0600688){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.temperature }}\end{tabular}}}}%
+    \put(0.32483758,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.oxygen_saturation }}\end{tabular}}}}%
+    \put(0.39476872,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glucometry }}\end{tabular}}}}%
+    \put(0.44852448,0.05986849){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.glassgow_total }}\end{tabular}}}}%
+    {% endif %}
     {% endfor %}
-    %Signos Vitales 2
+
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%

### 2022-08-30 ersteops/templates/printpdf/rendered_template.tex
add crum data, and fix vitals display

--- 2022-08-29 ersteops/templates/printpdf/rendered_template.tex
@@
     %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
+
+    %CRUM
+
+    \put(0.03139789,0.68674397){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{CRUM}\end{tabular}}}}%    
+    \put(0.03100834,0.67744828){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Folio: foliocrum 999999\end{tabular}}}}%
+    \put(0.03122157,0.66837832){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Hospital: magdalena de las salinas\end{tabular}}}}%
+    \put(0.03156192,0.65971048){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Médico: Dr. Perez\end{tabular}}}}%
+    \put(0.0314717,0.64991652){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}Notas: estas son las notas del crum veamos que pasa con u\end{tabular}}}}%
+
     %Times
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 58\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 60\end{tabular}}}}%
 
@@
     \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5\end{tabular}}}}%
-    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Moni Sanchez Jaime\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 7\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
     \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
@@
     %Padecimiento
-    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd asdasd asd asmdnasjd nasndklsand klasndkasndk snakdsnakldasnkd naskdnaskl \\nask ndklasdn klasndklas ndasnd\textquotesingle as \\dsa d \\asd asdas  \\d asdas dasd\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont asd asd asd asdasd asd asmdnasjd nasndklsand klasndkasndk snakdsnakldasnkd naskdnaskldnask ndklasdn klasndklas ndasnd\textquotesingle as \\dsa d \\asd asdas  \\d asdas dasd\end{tabular}}}}%
 
@@
 
-        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
     %inmovilizacion
-    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  \end{tabular}}}}%
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Columna Cervical\\Columna Toracica\\ \end{tabular}}}}%
 
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ NA\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ df  ghdfg dfgdfg SDf sdf sdf sdfsd\end{tabular}}}}%
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize as dasd asd asd asd asfsdfg dghdfh \end{tabular}}}}%
 
@@
     %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
-    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asdcas dasdasd\end{tabular}}}}%
 
@@
     % \put(0.48529688,0.50503129){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hipertensión arterial:\end{tabular}}}}%
-    \put(0.11758108,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
-    \put(0.14099679,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.11758108,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.14099679,0.16393908){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize as dasdasd\end{tabular}}}}%
 
@@
     % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sad asdasd\end{tabular}}}}%
     % %Cara
     % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asdas\end{tabular}}}}%
     % %Cuello
@@
     \put(0.65016698,0.50867338){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
     %Signos Vitales 1
 
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:26 \end{tabular}}}}%
+    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 80\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 16\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/70\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 37.3\end{tabular}}}}%
+    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 97\end{tabular}}}}%
+    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 104\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 12\end{tabular}} }}%
+
     %Signos Vitales 2
+
+    %Signos Vitales 2
+
+    \put(0.02662482,0.05996336){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:26\end{tabular}}}}%
+    \put(0.0575196,0.05986849){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 82\end{tabular}}}}%
+    \put(0.13048304,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 17\end{tabular}}}}%
+    \put(0.20938116,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/71\end{tabular}}}}%
+    \put(0.26551354,0.0600688){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 37.3\end{tabular}}}}%
+    \put(0.32483758,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
+    \put(0.39476872,0.06039818){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 105\end{tabular}}}}%
+    \put(0.44852448,0.05986849){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 13\end{tabular}}}}%
+
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%

### 2022-08-30 ersteops/printpdf/views.py

@@ -300,7 +300,7 @@ def get_medical_report(pk):
   medical_Report['json_inmovilization_type'] = list(eval(raw_medical_Report.inmovilization_type))
   medical_Report['fix_treatment'] = add_line_breaks(raw_medical_Report.treatment,49)
   medical_Report['fix_diagnostic_impresion'] = add_line_breaks(raw_medical_Report.diagnostic_impresion,38)
-  medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,41)  
+  medical_Report['fix_current_condition'] = add_line_breaks(raw_medical_Report.current_condition,85)  
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
   medical_Report['emergency_created_at'] = emergency.created_at.strftime('%Y-%m-%d')

### 2022-09-01 ersteops/ersteops/settings.py
fix aws problems

@@ -321,5 +321,6 @@ else:
   #DEFAULT_FILE_STORAGE = 'ersteops.custom_storages.MediaStorage' 
   DEFAULT_FILE_STORAGE = 'storages.backends.s3boto3.S3Boto3Storage'
   AWS_S3_FILE_OVERWRITE = False
-  AWS_DEFAULT_ACL = None
+  #AWS_DEFAULT_ACL = None
+  AWS_DEFAULT_ACL = 'bucket-owner-full-control'
   

### 2022-09-01 ersteops/paperless/views.py
update mail data

@@ -387,8 +387,8 @@ def Send_Mail_To(request,email_recive,pk,send_flag):
   #Send mail via smtp gmail server
   try:
     email = EmailMessage(
-      'Parte Medico Vida uno subject',
-      'Este es su parte medico body',
+      'Parte Medico Vida uno Folio {}'.format(pk),
+      'Ha recibido su parte médico digital del emisor EMERGENCIAS MEDICAS DE MEDICO SC con Folio:{}'.format(pk),
       'info@keepitsimple.com.mx',
       [ email_recive, ]
     )

### 2022-09-01 frontend/components/Geoposition/script.js
add marker to current position

@@ -41,6 +41,7 @@ export default {
         console.log(position.coords.longitude);
         this.paperless.service_geo_lat = position.coords.latitude;
         this.paperless.service_geo_lon = position.coords.longitude;
+        this.markers.push({ position: this.center });
       });
     },
   },

### 2022-09-06 ersteops/ersteops/settings.py
test correct settings for S3

@@ -321,6 +321,4 @@ else:
   #DEFAULT_FILE_STORAGE = 'ersteops.custom_storages.MediaStorage' 
   DEFAULT_FILE_STORAGE = 'storages.backends.s3boto3.S3Boto3Storage'
   AWS_S3_FILE_OVERWRITE = False
-  #AWS_DEFAULT_ACL = None
-  AWS_DEFAULT_ACL = 'bucket-owner-full-control'
-  
+  AWS_DEFAULT_ACL = None

### 2022-09-06 ersteops/paperless/views.py
add decorator and update email data

@@ -31,7 +31,11 @@ from printpdf.views import document_as_new_pdf
 
 from django.core.files.base import ContentFile, File
 
-#@method_decorator(login_required, name='dispatch')
+from django.contrib.auth.decorators import login_required
+from django.utils.decorators import method_decorator
+
+
+@method_decorator(login_required, name='dispatch')
 class MedicalReportNew(View):
   template_name = "paperless/new_medical_report_vue.html"
   #model = MedicalReport
@@ -132,7 +136,7 @@ class MedicalReportNew(View):
 
 
 
-#@method_decorator(login_required, name='dispatch')
+@method_decorator(login_required, name='dispatch')
 class MedicalReportList(ListView):
   #template_name = "paperless/paperless_list.html"
   template_name = "paperless/list_medical_reports.html"
@@ -153,7 +157,7 @@ class MedicalReportList(ListView):
 
     return qs
 
-
+@method_decorator(login_required, name='dispatch')
 class MedicalReportActive(ListView):
   template_name = "paperless/list_active_medical_reports.html"
   model = Emergency
@@ -183,6 +187,7 @@ class MedicalReportActive(ListView):
     #logger.info('[ QS MedicalReportActive! Actual Units;: {} ]'.format(qs_actual_unit))
     return qs
 
+@method_decorator(login_required, name='dispatch')
 class MedicalReportDetail(View):
   template_name = "paperless/detail_medical_report_2.html"
 
@@ -349,7 +354,8 @@ def new_medicalreport(request):
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
           pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
           pdf = pdf_file.read()
-          file_name = 'Parte_Medico_Vida_Uno_{}.pdf'.format(str(medicalReport.id))
+          d = medicalReport.created_at.strftime('%Y-%m-%d')
+          file_name = 'Parte_Medico_Vida_Uno_{}_{}.pdf'.format(d,str(medicalReport.id))
           medicalReport.final_report.save(file_name,ContentFile(pdf))
           #medicalReport.save()
           # emergency.save()

### 2022-09-08 ersteops/templates/printpdf/rendered_template.tex
add EOF

--- 2022-08-29 ersteops/templates/printpdf/rendered_template.tex
@@
     %\put(0.78960956,0.24450476){\includegraphics[scale=0.5]{client_signature}}%
+
+    %CRUM
+
     %Times
@@
     \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
-    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%
 
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 58\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 71\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize basica\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-002\end{tabular}}}}%
 
@@
     \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5\end{tabular}}}}%
-    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Moni Sanchez Jaime\end{tabular}}}}%
-    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
+    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize su casita 13\end{tabular}}}}%
 
@@
     %Padecimiento
-    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.11601621,0.2510955){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize le duele la pata tun, tun, tun!\end{tabular}}}}%
+    %\put(0.02265882,0.24439213){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont le duele la pata tun, tun, tun!\end{tabular}}}}%
 
     %Generales
-    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
-    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Hogar \end{tabular}}}}%
+    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Consulta Medica \end{tabular}}}}%
 
-      \put(0.3007691,0.47620579){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
+      \put(0.30180123,0.46556814){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X \end{tabular}}}}%
 
     %Trauma
-    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Craneal\\\fontfamily{lmss}\selectfont\scriptsize Craneoencefalico\\\end{tabular}}}}%
     %Motivo de Consulta
-    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cefalea\\\fontfamily{lmss}\selectfont\scriptsize Sincope\\\end{tabular}}}}%
     %to_fix
@@
 
-        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45522232,0.38124942){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
-
-        \put(0.45570433,0.35382833){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+        \put(0.45601685,0.41487724){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
 
     %inmovilizacion
-    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize  \end{tabular}}}}%
+    \put(0.38134429,0.33628328){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.7}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Columna Cervical\\ \end{tabular}}}}%
 
@@
     %\put(0.48529688,0.5272494){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Diabetes mellitus\end{tabular}}}}%
-    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
-    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.11758108,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
+    \put(0.14099679,0.17376971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize d as dasda sdsd\end{tabular}}}}%
 
@@
     % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd\end{tabular}}}}%
     % %Cara
     % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize a sdas dasd\end{tabular}}}}%
     % %Cuello
@@
     \put(0.65016698,0.50867338){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+
     %Signos Vitales 1
 
-    %Signos Vitales 2
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%

### 2022-09-09 ersteops/unit/migrations/0011_auto_20220909_1725.py
fix model

@@ -1,0 +1,18 @@
+# Generated by Django 2.2.27 on 2022-09-09 17:25
+
+from django.db import migrations, models
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('unit', '0010_auto_20220624_2014'),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name='unit',
+            name='crew',
+            field=models.ManyToManyField(blank=True, null=True, related_name='units', to='unit.CrewMember', verbose_name='Miembros de Tripulación'),
+        ),
+    ]

### 2022-09-09 ersteops/emergency/views.py
pause twillio funcionality

@@ -463,7 +463,7 @@ class EmergencyText(View):
             logger.info(content_paperless)
 
             content = content_patient + content_address + content_service + content_paperless
-            twillio_whatsap_send(content_paperless)
+            #twillio_whatsap_send(content_paperless)
 
         #except:
         except Exception as e:

### 2022-09-09 ersteops/emergency/views.py
fix comment

@@ -463,7 +463,7 @@ class EmergencyText(View):
             logger.info(content_paperless)
 
             content = content_patient + content_address + content_service + content_paperless
-            #twillio_whatsap_send(content_paperless)
+            # twillio_whatsap_send(content_paperless)
 
         #except:
         except Exception as e:

### 2022-09-28 ersteops/printpdf/views.py
add group medicatiosn function to display medications on template

@@ -291,7 +291,18 @@ def get_medical_report(pk):
   raw_medical_Report = MedicalReport.objects.get(id=pk)
   emergency = Emergency.objects.get(id=raw_medical_Report.service_code)
   medical_Report['json_physical_exploration'] = list(eval(raw_medical_Report.physical_exploration))
-  medical_Report['json_medications'] = list(eval(raw_medical_Report.medications))
+  json_medications = list(eval(raw_medical_Report.medications))
+  medical_Report['json_medications'] = json_medications
+
+  medical_Report['json_medications_solution'] = group_medications(json_medications,"Hemoderivado-Solucion")
+  medical_Report['json_medications_hemder'] = group_medications(json_medications,"Hemoderivado-Hemoderivado")
+
+  medical_Report['json_medications_desfib'] = group_medications(json_medications,"Cardiovascular-Desfibrilacion")
+  medical_Report['json_medications_cardio'] = group_medications(json_medications,"Cardiovascular-Cardioversion")
+
+  medical_Report['json_medications_farma'] = group_medications(json_medications,"Farmacologico-Farmaco")
+  medical_Report['json_medications_amina'] = group_medications(json_medications,"Farmacologico-Aminas")
+
   medical_Report['json_airway'] = list(eval(raw_medical_Report.airway)) 
   medical_Report['json_consultation_reason'] = list(eval(raw_medical_Report.consultation_reason))
   medical_Report['json_pupil_state_left'] = list(eval(raw_medical_Report.pupil_state_left))
@@ -311,6 +322,19 @@ def get_medical_report(pk):
   medical_Report['attention_final_grade'] = str(emergency.attention_final_grade).strip()
   #medical_Report['fix']
   return medical_Report
+
+def group_medications(input_data,filter):
+  l = []
+  logger.info('[ PRINTPDF! - group medications input_data-------------- {}]'.format(input_data))
+  for item in input_data:
+    d = {}
+    if item["medication_type"] == filter:
+      d["medication_name"] = item["medication_name"]
+      d["medication_dose"] = item["medication_dose"]
+      d["medication_hrs"] = item["medication_hrs"]
+      l.append(d)
+  logger.info('[ PRINTPDF! - group medications output_data-------------- {}]'.format(l))
+  return l
 
 def save_png(target_file,data_uri):
   have_signature_file = True

### 2022-09-28 ersteops/templates/printpdf/paperless_template.tex
add medications solution to template

@@
 
+    {% for item in content.json_medications_solution %}
+      {% if forloop.counter0 == 0 %}
+          \put(0.04964403,0.32745002){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11108429,0.32756971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+          \put(0.04964403,0.31750983){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11108429,0.31762951){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+          \put(0.04964403,0.30867309){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11108429,0.30879277){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
+    {{ content.medications }}
+
     %Antecedentes

### 2022-09-28 frontend/components/SignatureClient/script.js
add signature recived ok label

@@ -34,6 +34,7 @@ export default {
   // },
   data: () => ({
     paperless: window.erste.paperless,
+    signature_ok: '',
   }),
   methods: {
     async undo(e) {
@@ -50,6 +51,7 @@ export default {
       console.log(data);
       this.paperless.signature_client = data;
       console.log(this.paperless.signature_client);
+      this.signature_ok = 'Firma del paciente recibida';
       // alert(`Firma almacenada${this.paperless.signature_client}`);
     },
   },

### 2022-09-28 ersteops/templates/printpdf/rendered_template.tex
updater templates

--- 2022-08-30 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 59\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 72\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Basica\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ABC-123\end{tabular}}}}%
 
@@
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
-    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 0\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 15\end{tabular}}}}%
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
@@
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ estas son las descripciones de lesione \\ sadas dasd asasd ans,.dasn asd asd a \\s asd asd asd asd asadsd asdas asd as \\ asd asd asd asdas das as asd,.mn,.m, \\asdm .dasd \\asd asd asdasd asd as\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ NA\end{tabular}}}}%
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize este es el tratamiento que al fional falla,debemo \\ hacsr que no fale por que si falla ya valio ber \\a las calmadas y asi \\esta es otra linea del trat \\moento a ver cuantos caracteres son \\ \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
 
     %Medicamentos (to_fix)
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]\end{tabular}}}}%
     %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hemoderivado-Solucion - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 123 - 0 hrs\\Cardiovascular-Desfibrilacion - 124 - 0 hrs\\Cardiovascular-Cardioversion - 125 - 0 hrs\\\end{tabular}}}}%
+
+          \put(0.04964403,0.32745002){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 120\end{tabular}}}}%
+          \put(0.11108429,0.32756971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 1\end{tabular}}}}%
+
+    [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]
 
@@
     \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
-    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize patitas\end{tabular}}}}%
+    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize dasdasd\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sin tum\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize el faisan\end{tabular}}}}%
 

### 2022-09-29 ersteops/templates/printpdf/paperless_template.tex
update medications

@@
 
+    {% for item in content.json_medications_hemder %}
+      {% if forloop.counter0 == 0 %}
+          \put(0.04940118,0.2888225){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11084145,0.28894218){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+          \put(0.04940118,0.27893225){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11023136,0.27905193){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+          \put(0.04940118,0.26982475){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.10959944,0.26994443){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
+    {% for item in content.json_medications_desfib %}
+      {% if forloop.counter0 == 0 %}
+          \put(0.1589072,0.32726279){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.21626297,0.3273940){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+          \put(0.15916412,0.31839182){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.11023136,0.27905193){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+          \put(0.1584999,0.30822806){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.21585568,0.30835933){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
+    {% for item in content.json_medications_cardio %}
+      {% if forloop.counter0 == 0 %}
+          \put(0.15866873,0.2898937){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.21668871,0.2898937){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+          \put(0.15887895,0.27981739){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+          \put(0.15887895,0.27981739){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+          \put(0.21689892,0.27981739){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
+    {% for item in content.json_medications_farma %}
+      {% if forloop.counter0 == 0 %}
+        \put(0.26321649,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30511372,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33483843,0.32720095){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+        \put(0.26342897,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3053262,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33505092,0.31823051){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+        \put(0.26308947,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3049867,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33471142,0.30798187){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
+    {% for item in content.json_medications_amina %}
+      {% if forloop.counter0 == 0 %}
+        \put(0.26517407,0.28858281){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30543707,0.28852296){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33395328,0.28858473){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 1 %}
+        \put(0.26491781,0.27987623){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30518081,0.27981639){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33369702,0.27987816){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+      {% if forloop.counter0 == 2 %}
+        \put(0.26516689,0.27001966){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3054299,0.26995982){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.3339461,0.27002158){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+      {% endif %}
+    {% endfor %}
+
     {{ content.medications }}

### 2022-09-29 ersteops/printpdf/views.py
cleanup code

@@ -293,16 +293,12 @@ def get_medical_report(pk):
   medical_Report['json_physical_exploration'] = list(eval(raw_medical_Report.physical_exploration))
   json_medications = list(eval(raw_medical_Report.medications))
   medical_Report['json_medications'] = json_medications
-
   medical_Report['json_medications_solution'] = group_medications(json_medications,"Hemoderivado-Solucion")
   medical_Report['json_medications_hemder'] = group_medications(json_medications,"Hemoderivado-Hemoderivado")
-
   medical_Report['json_medications_desfib'] = group_medications(json_medications,"Cardiovascular-Desfibrilacion")
   medical_Report['json_medications_cardio'] = group_medications(json_medications,"Cardiovascular-Cardioversion")
-
   medical_Report['json_medications_farma'] = group_medications(json_medications,"Farmacologico-Farmaco")
   medical_Report['json_medications_amina'] = group_medications(json_medications,"Farmacologico-Aminas")
-
   medical_Report['json_airway'] = list(eval(raw_medical_Report.airway)) 
   medical_Report['json_consultation_reason'] = list(eval(raw_medical_Report.consultation_reason))
   medical_Report['json_pupil_state_left'] = list(eval(raw_medical_Report.pupil_state_left))
@@ -325,7 +321,6 @@ def get_medical_report(pk):
 
 def group_medications(input_data,filter):
   l = []
-  logger.info('[ PRINTPDF! - group medications input_data-------------- {}]'.format(input_data))
   for item in input_data:
     d = {}
     if item["medication_type"] == filter:
@@ -333,7 +328,6 @@ def group_medications(input_data,filter):
       d["medication_dose"] = item["medication_dose"]
       d["medication_hrs"] = item["medication_hrs"]
       l.append(d)
-  logger.info('[ PRINTPDF! - group medications output_data-------------- {}]'.format(l))
   return l
 
 def save_png(target_file,data_uri):

### 2022-09-29 ersteops/printpdf/views.py
improve coding

@@ -322,11 +322,12 @@ def get_medical_report(pk):
 def group_medications(input_data,filter):
   l = []
   for item in input_data:
-    d = {}
     if item["medication_type"] == filter:
-      d["medication_name"] = item["medication_name"]
-      d["medication_dose"] = item["medication_dose"]
-      d["medication_hrs"] = item["medication_hrs"]
+      d = {
+        "medication_name" : item.get("medication_name",""),
+        "medication_dose" : item.get("medication_dose",""),
+        "medication_hrs" : item.get("medication_hrs","")
+      }
       l.append(d)
   return l
 

### 2022-09-30 ersteops/paperless/dict_fields.py
add submit hide and spinner

@@ -95,4 +95,5 @@ MedicalReportDict = {
 "crew_operator":"",
 "signature_client":"",
 "signature_medic":"",
+"submited": "False",
 }

### 2022-10-01 ersteops/templates/printpdf/paperless_template.tex
remove no need content

@@
       {% if forloop.counter0 == 0 %}
-        \put(0.26321649,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.30511372,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.33483843,0.32720095){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26321649,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30511372,0.32734768){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33483843,0.32720095){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
       {% if forloop.counter0 == 1 %}
-        \put(0.26342897,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.3053262,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.33505092,0.31823051){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26342897,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3053262,0.31837723){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33505092,0.31823051){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
       {% if forloop.counter0 == 2 %}
-        \put(0.26308947,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.3049867,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.33471142,0.30798187){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26308947,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3049867,0.3081286){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33471142,0.30798187){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
@@
       {% if forloop.counter0 == 0 %}
-        \put(0.26517407,0.28858281){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.30543707,0.28852296){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.33395328,0.28858473){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26517407,0.28858281){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30543707,0.28852296){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33395328,0.28858473){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
       {% if forloop.counter0 == 1 %}
-        \put(0.26491781,0.27987623){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.30518081,0.27981639){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.33369702,0.27987816){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26491781,0.27987623){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.30518081,0.27981639){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.33369702,0.27987816){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
       {% if forloop.counter0 == 2 %}
-        \put(0.26516689,0.27001966){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_name }}\end{tabular}}}}%
-        \put(0.3054299,0.26995982){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_dose }}\end{tabular}}}}%
-        \put(0.3339461,0.27002158){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{ item.medication_hrs }}\end{tabular}}}}%
+        \put(0.26516689,0.27001966){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_name }}\end{tabular}}}}%
+        \put(0.3054299,0.26995982){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_dose }}\end{tabular}}}}%
+        \put(0.3339461,0.27002158){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{ item.medication_hrs }}\end{tabular}}}}%
       {% endif %}
     {% endfor %}
-
-    {{ content.medications }}
 

### 2022-10-01 ersteops/templates/printpdf/rendered_template.tex
update medications

@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 72\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 76\end{tabular}}}}%
 
@@
     \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 15\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
@@
     %Medicamentos (to_fix)
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]\end{tabular}}}}%
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont []\end{tabular}}}}%
     %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont la medi\end{tabular}}}}%
-    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Hemoderivado-Solucion - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 120 - 0 hrs\\Hemoderivado-Hemoderivado - 123 - 0 hrs\\Cardiovascular-Desfibrilacion - 124 - 0 hrs\\Cardiovascular-Cardioversion - 125 - 0 hrs\\\end{tabular}}}}%
-
-          \put(0.04964403,0.32745002){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 120\end{tabular}}}}%
-          \put(0.11108429,0.32756971){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 1\end{tabular}}}}%
-
-    [\{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Solucion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 1\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 120\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 2\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Hemoderivado-Hemoderivado\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 123\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 3\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Desfibrilacion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 124\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 4\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} , \{ \textquotesingle medication\textunderscore type\textquotesingle : \textquotesingle Cardiovascular-Cardioversion\textquotesingle , \textquotesingle medication\textunderscore name\textquotesingle : \textquotesingle 125\textquotesingle , \textquotesingle medication\textunderscore dose\textquotesingle : \textquotesingle 5\textquotesingle , \textquotesingle medication\textunderscore hrs\textquotesingle : 0\} ]
+    %\put(0.0159714,0.27918911){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont \end{tabular}}}}%
 
@@
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize dasdasd\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sin tum\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Con Tum\end{tabular}}}}%
     \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize el faisan\end{tabular}}}}%
+
+      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
+      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+
+    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
+    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 

### 2022-10-12 ersteops/templates/printpdf/paperless_template.tex
use little template strategy

@@
     %Times
-    \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.emergency_created_at}}\end{tabular}}}}%
-    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.unit_dispatched_time}}\end{tabular}}}}%
-    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.arrival_time}}\end{tabular}}}}%
-    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.attention_time}}\end{tabular}}}}%
-    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.final_emergency_time}}\end{tabular}}}}%
+    {% include "printpdf/latex_text.html" with position="0.03117976,0.58432043" font_size="tiny" content_text=content.emergency_created_at %}
+    {% include "printpdf/latex_text.html" with position="0.06427789,0.58446308" font_size="tiny" content_text=content.unit_dispatched_time %}
+    {% include "printpdf/latex_text.html" with position="0.10029604,0.58387567" font_size="tiny" content_text=content.arrival_time %}
+    {% include "printpdf/latex_text.html" with position="0.13910523,0.58360406" font_size="tiny" content_text=content.attention_time %}
+    {% include "printpdf/latex_text.html" with position="0.17543913,0.58380438" font_size="tiny" content_text=content.final_emergency_time %}
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit}}\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_type}}\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.service_unit_type}}\end{tabular}}}}%
     \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.service_unit_plate}}\end{tabular}}}}%
@@
     %Paciente
-    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.erste_code}} - {{content.odoo_client_name}}\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny {{content.erste_code}} - {{content.odoo_client_name}}\end{tabular}}}}%
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.patient_phone}}\end{tabular}}}}%

### 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
use little template strategy

@@
     \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 2022-07-22\end{tabular}}}}%
+
     \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 76\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 77\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Basica\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ABC-123\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
 
     %Paciente
-    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny F55 - Lillia Sanchez Jaime\end{tabular}}}}%
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
@@
 
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 19:01 \end{tabular}}}}%
+    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 129/40\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
+    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
+    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 6\end{tabular}} }}%
+
+    %Signos Vitales 2
+
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
@@
     \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize patitas\end{tabular}}}}%
-    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize dasdasd\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Con Tum\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize el faisan\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
+    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%
 

### 2022-10-12 ersteops/templates/printpdf/paperless_template.tex
add little template strategy for emergency grade

@@
     {% if content.attention_final_grade == 'G0' %}
-    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+      {% include "printpdf/latex_text.html" with position="0.37115545,0.574256" font_size="scriptsize" content_text="X" %}
     {% endif %}
     {% if content.attention_final_grade == 'G1' %}
-    \put(0.42545332,0.57475133){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+      {% include "printpdf/latex_text.html" with position="0.42545332,0.57475133" font_size="scriptsize" content_text="X" %}
     {% endif %}
     {% if content.attention_final_grade == 'G2' %}
-    \put(0.4811341,0.5742217){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+      {% include "printpdf/latex_text.html" with position="0.4811341,0.5742217" font_size="scriptsize" content_text="X" %}
     {% endif %}

### 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
add little template strategy for emergency grade
fix ui spinner

--- 2022-10-01 ersteops/templates/printpdf/rendered_template.tex
@@
     \put(0.03117976,0.58432043){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 2022-07-22\end{tabular}}}}%
+
     \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+
     \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%
 
-    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+      \put(0.37115545,0.574256){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Basica\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny Basica\end{tabular}}}}%
     \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ABC-123\end{tabular}}}}%
@@
     %Paciente
-    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize F55 - Lillia Sanchez Jaime\end{tabular}}}}%
+    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny F55 - Lillia Sanchez Jaime\end{tabular}}}}%
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%

### 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
fix time to display

--- 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
@@
 
-    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%
+      \put(0.37115545,0.574256){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X\end{tabular}}}}%
 
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 77\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 78\end{tabular}}}}%
 
@@
     \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
-    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
-    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
+    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 0\end{tabular}}}}%
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
@@
 
-    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 19:01 \end{tabular}}}}%
-    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
-    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120\end{tabular}}}}%
-    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 129/40\end{tabular}}}}%
-    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
-    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
-    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
-    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 6\end{tabular}} }}%
-
-    %Signos Vitales 2
-
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
@@
     \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%
-
-      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
-      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
-
-    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
-    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
-    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
 

### 2022-10-12 ersteops/printpdf/views.py

@@ -311,10 +311,10 @@ def get_medical_report(pk):
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
   medical_Report['emergency_created_at'] = emergency.created_at.strftime('%Y-%m-%d')
-  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.strftime('%H:%M')
-  medical_Report['arrival_time'] = emergency.arrival_time.strftime('%H:%M')
-  medical_Report['attention_time'] = emergency.attention_time.strftime('%H:%M')
-  medical_Report['final_emergency_time'] = emergency.final_emergency_time.strftime('%H:%M')
+  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.astimezone().strftime('%H:%M')
+  medical_Report['arrival_time'] = emergency.arrival_time.astimezone().strftime('%H:%M')
+  medical_Report['attention_time'] = emergency.attention_time.astimezone().strftime('%H:%M')
+  medical_Report['final_emergency_time'] = emergency.final_emergency_time.astimezone().strftime('%H:%M')
   medical_Report['attention_final_grade'] = str(emergency.attention_final_grade).strip()
   #medical_Report['fix']
   return medical_Report

### 2022-10-12 ersteops/printpdf/views.py
test datetime conversions

@@ -311,7 +311,7 @@ def get_medical_report(pk):
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
   medical_Report['emergency_created_at'] = emergency.created_at.strftime('%Y-%m-%d')
-  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.astimezone().strftime('%H:%M')
+  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.strftime('%H:%M')
   medical_Report['arrival_time'] = emergency.arrival_time.astimezone().strftime('%H:%M')
   medical_Report['attention_time'] = emergency.attention_time.astimezone().strftime('%H:%M')
   medical_Report['final_emergency_time'] = emergency.final_emergency_time.astimezone().strftime('%H:%M')

### 2022-10-12 ersteops/printpdf/views.py
fix utc dattime issue

@@ -31,6 +31,10 @@ logger = logging.getLogger('django_info')
 
 import base64
 
+#Set timezone requirments
+from django.utils import timezone
+import pytz
+TIME_ZONE = "America/Mexico_City"
 
 # Create your views here.
 # generate pdf for screen
@@ -286,7 +290,11 @@ def escape_text(s):
 
 
 def get_medical_report(pk):
-  #medical_Report = MedicalReport.get(id=pk)
+
+  #Set time zone
+  mex =  pytz.timezone(TIME_ZONE)
+
+
   medical_Report = MedicalReport.objects.filter(id=pk).values()[0]
   raw_medical_Report = MedicalReport.objects.get(id=pk)
   emergency = Emergency.objects.get(id=raw_medical_Report.service_code)
@@ -311,10 +319,10 @@ def get_medical_report(pk):
   medical_Report['have_client_signature'] = save_png('client_signature',raw_medical_Report.signature_client)
   medical_Report['have_medic_signature'] = save_png('signature_medic',raw_medical_Report.signature_medic)
   medical_Report['emergency_created_at'] = emergency.created_at.strftime('%Y-%m-%d')
-  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.strftime('%H:%M')
-  medical_Report['arrival_time'] = emergency.arrival_time.astimezone().strftime('%H:%M')
-  medical_Report['attention_time'] = emergency.attention_time.astimezone().strftime('%H:%M')
-  medical_Report['final_emergency_time'] = emergency.final_emergency_time.astimezone().strftime('%H:%M')
+  medical_Report['unit_dispatched_time'] = emergency.unit_dispatched_time.astimezone(mex).strftime('%H:%M')
+  medical_Report['arrival_time'] = emergency.arrival_time.astimezone(mex).strftime('%H:%M')
+  medical_Report['attention_time'] = emergency.attention_time.astimezone(mex).strftime('%H:%M')
+  medical_Report['final_emergency_time'] = emergency.final_emergency_time.astimezone(mex).strftime('%H:%M')
   medical_Report['attention_final_grade'] = str(emergency.attention_final_grade).strip()
   #medical_Report['fix']
   return medical_Report

### 2022-10-14 ersteops/templates/printpdf/rendered_template.tex
remove files
put back to trace errors
add prevent leaving paperless without saving!

@@
 
-    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.06427789,0.58446308){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 20:23\end{tabular}}}}%
 
-    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.10029604,0.58387567){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 20:23\end{tabular}}}}%
 
-    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 01:23\end{tabular}}}}%
+    \put(0.13910523,0.58360406){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 20:23\end{tabular}}}}%
 
-    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 00:07\end{tabular}}}}%
+    \put(0.17543913,0.58380438){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 19:07\end{tabular}}}}%
 
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 78\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 81\end{tabular}}}}%
 
@@
     \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdfsdf\end{tabular}}}}%
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
     \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%
 

### 2022-10-14 frontend/components/MedicalReport/script.js

@@ -42,6 +42,7 @@ export default {
       { text: 'Miosis', value: 'Miosis' },
       { text: 'Anisocoria', value: 'Anisocoria' },
     ],
+    isEditing: true,
     // const canvas = document.querySelector("canvas");
     // const signaturePad = new SignaturePad(canvas);
   }),
@@ -52,8 +53,31 @@ export default {
     SignatureMedic,
     Medications,
   },
+
+  beforeMount() {
+    window.addEventListener('beforeunload', this.preventNav);
+    this.$once('hook:beforeDestroy', () => {
+      window.removeEventListener('beforeunload', this.preventNav);
+    });
+  },
+
+  beforeRouteLeave(to, from, next) {
+    if (this.isEditing) {
+      if (!window.confirm('Salir sin guardar?')) {
+        return;
+      }
+    }
+    next();
+  },
+
   methods: {
     ...mapActions('newMedicalReport', ['createMedicalReport']),
+
+    preventNav(event) {
+      if (!this.isEditing) return;
+      event.preventDefault();
+      event.returnValue = '';
+    },
 
     async submit(e) {
       // e.preventDefault();
@@ -82,6 +106,7 @@ export default {
       try {
         e.stopPropagation();
         e.preventDefault();
+        this.isEditing = false;
         this.paperless.submited = 'True';
         // var form = $(this);
         // var jsonForm= form.serialize();

### 2022-10-14 ersteops/templates/printpdf/rendered_template.tex
fix typo solution from https://austingil.com/prevent-browser-refresh-url-changes-route-navigation-vue/

@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 81\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 83\end{tabular}}}}%
 
@@
     \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdfsdf\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
     \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
+
+      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
+      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%
+
+    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
+    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
+    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%
 

### 2022-10-14 frontend/components/MedicalReport/script.js

@@ -63,7 +63,7 @@ export default {
 
   beforeRouteLeave(to, from, next) {
     if (this.isEditing) {
-      if (!window.confirm('Salir sin guardar?')) {
+      if (!window.confirm('Salir sin guardar ?')) {
         return;
       }
     }

### 2022-10-18 ersteops/paperless/views.py
clean up  logic

@@ -231,13 +231,14 @@ def new_medicalreport(request):
     #logger.info('[ NEW MEWDICAL REPORT: -3- {} ]'.format(current_user))
     #logger.info('[ NEW MEWDICAL REPORT DATA: -4- {} ]'.format(data))
     #if 'id' in data and 'timer_type' in data :
+    # Save data from FE to MODEL
     if 'paperless' in data :
       #qs =  Emergency.objects.get(pk = pl_emergency_id)
       try:
           logger.info('[ NEW MEWDICAL REPORT DATA: -5- {} ]'.format(data['paperless']))
           vue_data=json.loads(data['paperless'])
           logger.info('[ NEW MEWDICAL REPORT DATA: -6- {} ]'.format(vue_data['service_code']))
-          logger.info('[ NEW MEWDICAL REPORT DATA: -7- {} ]'.format(vue_data['signature_client']))
+          #logger.info('[ NEW MEWDICAL REPORT DATA: -7- {} ]'.format(vue_data['signature_client']))
           qs = Emergency.objects.get(id=vue_data['service_code'])
           medicalReport = MedicalReport.objects.create(
           odoo_client = qs.odoo_client,
@@ -349,16 +350,22 @@ def new_medicalreport(request):
           odoo_client_name = qs.partner_name,
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
-          messages.info(request, "Parte Medico Sending email an generating pdf!!!")
-          Send_Mail_To(request,vue_data['email'],medicalReport.id,vue_data['send_email'])
+          messages.info(request, "Parte Medico Generating pdf!!!")
+          #pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.pdf/'
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
-          pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
-          pdf = pdf_file.read()
-          d = medicalReport.created_at.strftime('%Y-%m-%d')
-          file_name = 'Parte_Medico_Vida_Uno_{}_{}.pdf'.format(d,str(medicalReport.id))
-          medicalReport.final_report.save(file_name,ContentFile(pdf))
-          #medicalReport.save()
-          # emergency.save()
+          pdf = document_as_new_pdf(request,medicalReport.id)
+
+          if pdf:
[…]

### 2022-10-18 ersteops/printpdf/views.py
add self notification in case of pdf generating

@@ -36,6 +36,8 @@ from django.utils import timezone
 import pytz
 TIME_ZONE = "America/Mexico_City"
 
+from django.core.mail import EmailMessage
+
 # Create your views here.
 # generate pdf for screen
 def document_as_pdf(request,pk):
@@ -67,6 +69,7 @@ def document_as_pdf(request,pk):
     return r
   else:
     #print("PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
+    emailNotifryError(pk)
     logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     return redirect('/paperless/')
@@ -99,11 +102,39 @@ def document_as_new_pdf(request,pk):
     #r.write(pdf)
     return pdf
   else:
+    emailNotifryError(pk)
     #print("PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
     logger.info('[ PRINTPDF! - PDF Error!!! ckeck /templates/printpdf/rendered_template.log]') 
     messages.error(request, "PDF Error!!! ckeck /templates/printpdf/rendered_template.log")
-    return redirect('/paperless/')
+    #return redirect('/paperless/')
+    return False
 
+
+def emailNotifryError(pk):
+    try:
+      email = EmailMessage(
+        'Parte Medico Vida uno Folio {}'.format(pk),
+        'Ha recibido su parte médico digital del emisor EMERGENCIAS MEDICAS DE MEDICO SC con Folio:{}'.format(pk),
+        'info@keepitsimple.com.mx',
+        [ 'juanmanuelriverom@gmail.com', ]
+      )
+      pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.log/'
+      tempdir = settings.BASE_DIR+'/templates/printpdf/'
+      log_file = open(os.path.join(tempdir, 'rendered_template.log'), 'rb')
+      pdf = log_file.read()
+      file_name = 'Parte_Medico_Vida_Uno_{}.log'.format(str(pk))
+      #attach log file
+      email.attach(file_name,pdf,'application/txt')
+      # attach tex file
+      tex_file = open(os.path.join(tempdir, 'rendered_template.tex'), 'rb')
+      tex = tex_file.read()
[…]

### 2022-10-18 frontend/components/MedicalReport/script.js
fix fe notificatiion

@@ -134,6 +134,7 @@ export default {
         });
         this.paperless.submited = 'False';
       } catch (err) {
+        this.paperless.submited = 'False';
         this.$emit('error', err);
         this.$notify({
           text: `No se pudo crear el parte medico - ${err}`,

### 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
update files

@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 83\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 113\end{tabular}}}}%
 
@@
    	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
 
@@
     \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
-    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
+    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdfsdf\end{tabular}}}}%
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%

### 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
add email sent to preview

--- 2022-10-14 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 83\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 116\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny SOPORTE\end{tabular}}}}%
     \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
@@
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
-    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASDAS DASDAS casdcas\end{tabular}}}}%
 
@@
     %Generales
-    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Hogar \end{tabular}}}}%
     \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
@@
     %Trauma
-    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Craneal\\\end{tabular}}}}%
     %Motivo de Consulta
@@
 
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:39 \end{tabular}}}}%
+    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 60\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/80\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
+    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
+    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 3\end{tabular}} }}%
+
+    %Signos Vitales 2
+
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%

### 2022-10-18 ersteops/paperless/views.py

@@ -363,6 +363,8 @@ def new_medicalreport(request):
             Send_Mail_To(request,vue_data['email'],medicalReport.id,vue_data['send_email'],pdf)
             d = medicalReport.created_at.strftime('%Y-%m-%d')
             file_name = 'Parte_Medico_Vida_Uno_{}_{}.pdf'.format(d,str(medicalReport.id))
+            medicalReport.email_sent = True
+            medicalReport.save()
             medicalReport.final_report.save(file_name,ContentFile(pdf))
             #medicalReport.save()
             # emergency.save()
@@ -371,8 +373,11 @@ def new_medicalreport(request):
           response.status_code = 202
           return response
       except Exception as e:
-          logger.error("[Create Medical Report View ERROR]: {}, type: {}".format(e, type(e)))
-          return bad_response
+          medicalReport.email_sent = False
+          medicalReport.save()
+          logger.error("[Create Medical Report View ERROR SENDING EMAIL]: {}, type: {}".format(e, type(e)))
+          #return bad_response
+          return redirect('/paperless')
 
       #qs.medical_report = medicalReport
       #qs.save()

### 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
add pattern input format

--- 2022-10-14 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 83\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 118\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny SOPORTE\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
 
@@
 
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:51 \end{tabular}}}}%
+    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 10\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 240/10\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
+    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
+    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 3\end{tabular}} }}%
+
+    %Signos Vitales 2
+
     %\put(0.48899072,0.59441199){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont 12:41\end{tabular}}}}%
@@
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo``\end{tabular}}}}%
     \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%

### 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
update notification email functionality

--- 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 116\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 120\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny SOPORTE\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
 
@@
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
-    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASDAS DASDAS casdcas\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asdas dasd das\end{tabular}}}}%
 
@@
     \put(0.04438815,0.46496172){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Hogar \end{tabular}}}}%
-    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.04438815,0.39751941){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Urgencias \end{tabular}}}}%
 
@@
     %Motivo de Consulta
-    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+    \put(0.13358814,0.46425894){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cefalea\\\end{tabular}}}}%
     %to_fix
@@
     \put(0.32505266,0.47551987){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
+
+        \put(0.43392821,0.44715646){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+        \put(0.43430823,0.41551969){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
+
+        \put(0.45563683,0.44651401){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\textbf{X}\end{tabular}}}}%
 
@@
     %Impresion diagnostica
-    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ NA\end{tabular}}}}%
+    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\ sdfgdfgh fghgh\end{tabular}}}}%
     %Tratamiento
-    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%
+    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize hj jkhljkl \end{tabular}}}}%
 
@@
     % \put(0.48349046,0.31358676){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cabeza\end{tabular}}}}%
-    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.62779907){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.62786673){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asd asd\end{tabular}}}}%
     % %Cara
     % \put(0.48349046,0.29763166){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Cara\end{tabular}}}}%
-    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Si\end{tabular}}}}%
-    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
+    \put(0.5916532,0.6184675){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize No\end{tabular}}}}%
+    \put(0.61206298,0.61853516){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize asd asdas d\end{tabular}}}}%
     % %Cuello
@@
 
-    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:39 \end{tabular}}}}%
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 18:41 \end{tabular}}}}%
     \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
     \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 60\end{tabular}}}}%
-    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/80\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/60\end{tabular}}}}%
     \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%

### 2022-10-18 ersteops/ersteops/settings.py

@@ -302,7 +302,7 @@ EMAIL_HOST_PASSWORD = os.environ['EMAIL_HOST_PASSWORD'] #past the key or passwor
 EMAIL_PORT = os.environ['EMAIL_PORT']
 EMAIL_USE_TLS = os.environ['EMAIL_USE_TLS']
 DEFAULT_FROM_EMAIL = os.environ['DEFAULT_FROM_EMAIL']
-
+NOTIFY_ERROR_EMAIL = os.environ['NOTIFY_ERROR_EMAIL']
 
 MEDIA_LOCAL = ast.literal_eval(os.environ['PDF_MEDIA_LOCAL'])
 # Define if media storage is local or S3

### 2022-10-18 ersteops/printpdf/views.py

@@ -114,9 +114,9 @@ def emailNotifryError(pk):
     try:
       email = EmailMessage(
         'Parte Medico Vida uno Folio {}'.format(pk),
-        'Ha recibido su parte médico digital del emisor EMERGENCIAS MEDICAS DE MEDICO SC con Folio:{}'.format(pk),
+        'Notificacion de error en generacion del parte medico PDF: {}'.format(pk),
         'info@keepitsimple.com.mx',
-        [ 'juanmanuelriverom@gmail.com', ]
+        [ settings.NOTIFY_ERROR_EMAIL ]
       )
       pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.log/'
       tempdir = settings.BASE_DIR+'/templates/printpdf/'

### 2022-10-19 ersteops/templates/printpdf/rendered_template.tex
clean comments

--- 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 116\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 122\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny SOPORTE\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
     \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
@@
     \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
-    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize ASDAS DASDAS casdcas\end{tabular}}}}%
+    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 10x\textquotesingle\end{tabular}}}}%
 
@@
     %Trauma
-    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Craneal\\\end{tabular}}}}%
+    \put(0.23206628,0.45573384){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{0.8}\smash{\begin{tabular}[t]{l}\end{tabular}}}}%
     %Motivo de Consulta
@@
 
-    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:39 \end{tabular}}}}%
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 19:09 \end{tabular}}}}%
     \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
-    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 60\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 10\end{tabular}}}}%
     \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/80\end{tabular}}}}%
@@
     \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
-    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 3\end{tabular}} }}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 8\end{tabular}} }}%
 
@@
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
-    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo``\end{tabular}}}}%
+    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%
 

### 2022-10-19 ersteops/paperless/views.py

@@ -351,7 +351,6 @@ def new_medicalreport(request):
           )
           messages.info(request, "Parte Medico Guardado correctamente!!!")
           messages.info(request, "Parte Medico Generating pdf!!!")
-          #pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.pdf/'
           tempdir = settings.BASE_DIR+'/templates/printpdf/'
           pdf = document_as_new_pdf(request,medicalReport.id)
 
@@ -403,16 +402,6 @@ def not_find_on_list(my_list_Dict, what_to_search):
 
 def Send_Mail_To(request,email_recive,pk,send_flag,pdf):
   #Send mail via smtp gmail server
-  #pdf_to_attach = settings.BASE_DIR+'/templates/printpdf/rendered_template.pdf/'
-  #tempdir = settings.BASE_DIR+'/templates/printpdf/'
-  #pdf = document_as_new_pdf(request,pk)
-  # Test if pdf was generated correctly
-  #try:
-  #  pdf_file = open(os.path.join(tempdir, 'rendered_template.pdf'), 'rb')
-  #except Exception as e:
-  #  send_flag = False
-  #  logger.error("[Create Medical Report Email ERROR not pdf]: {}, type: {}".format(e, type(e)))
-  #  return bad_response
   try:
     email = EmailMessage(
       'Parte Medico Vida uno Folio {}'.format(pk),

### 2022-10-19 ersteops/templates/printpdf/rendered_template.tex
clean comments

--- 2022-10-18 ersteops/templates/printpdf/rendered_template.tex
@@
     %Folio
-    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 118\end{tabular}}}}%
+    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 124\end{tabular}}}}%
 
@@
     \put(0.20804855,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize M011\end{tabular}}}}%
-   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny SOPORTE\end{tabular}}}}%
-    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-005\end{tabular}}}}%
+   	\put(0.32826955,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny ASISTENCIA BASICA\end{tabular}}}}%
+    \put(0.43247465,0.55435574){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize QPR-001\end{tabular}}}}%
 
@@
 
-    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 15:51 \end{tabular}}}}%
+    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 16:22 \end{tabular}}}}%
     \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
-    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 10\end{tabular}}}}%
-    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 240/10\end{tabular}}}}%
-    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
+    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 60\end{tabular}}}}%
+    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120/80\end{tabular}}}}%
+    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 25\end{tabular}}}}%
     \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
     \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
-    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 3\end{tabular}} }}%
+    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 6\end{tabular}} }}%
 
@@
     \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
-    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo``\end{tabular}}}}%
+    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
     \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%

### 2022-10-19 ersteops/paperless/views.py

@@ -164,24 +164,13 @@ class MedicalReportActive(ListView):
 
   def get_queryset(self):
     current_user = self.request.user
-    #actual_user = CrewMember.objects.get( user= current_user)
-    #actual_date = []
-    #actual_date.append(datetime.now().date())
-    #actual_date = datetime.now().date() 
-    #qs_actual_unit = TodayUnitDoctor.objects.filter(unit_date__gte=actual_date)
-
-    #print("Actual units: {}".format(qs_actual_unit))
     qs = Emergency.objects.filter(is_active = True)
-    #qs.filter(units is not null)
     emergency_list = []
     for emergency in qs:
       if emergency.units.count() >0:
         if not emergency.medical_report:
           emergency_list.append(emergency.id)
-
     qs = Emergency.objects.filter(id__in= emergency_list)
-    #qs.filter(medical_report__isnull= True)
-
     logger.info('[ QS MedicalReportActive! Current User: {} ]'.format(current_user))
     logger.info('[ QS MedicalReportActive! Emegrencies with units: {} ]'.format(emergency_list))
     #logger.info('[ QS MedicalReportActive! Actual Units;: {} ]'.format(qs_actual_unit))
@@ -204,13 +193,7 @@ class MedicalReportDetail(View):
 
     return render(request, self.template_name,{"data":qs,})
 
-#   def post (self, request, *args, **kwargs):
-#     return redirect('/paperless/')
 
-
-
-# Update Timer Functionality
-#@csrf_exempt
 @csrf_protect
 def new_medicalreport(request):
     ''' '''
@@ -225,12 +208,7 @@ def new_medicalreport(request):
         logger.info('[ NEW MEWDICAL REPORT -2- Not body: {} ]'.format(current_user))
         logger.info('[ NEW MEWDICAL REPORT DATA: {} ]'.format(data))
         return bad_response
-
     data = json.loads(request.body.decode('utf-8'))
-
-    #logger.info('[ NEW MEWDICAL REPORT: -3- {} ]'.format(current_user))
-    #logger.info('[ NEW MEWDICAL REPORT DATA: -4- {} ]'.format(data))
-    #if 'id' in data and 'timer_type' in data :
     # Save data from FE to MODEL
     if 'paperless' in data :
       #qs =  Emergency.objects.get(pk = pl_emergency_id)
@@ -365,8 +343,6 @@ def new_medicalreport(request):
             medicalReport.email_sent = True
             medicalReport.save()
[…]
